### 2020-08-05 paper/main.tex
Startet paper.

\documentclass[11pt, DIV=12]{scrartcl}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage[numbers]{natbib}

\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{url}
\usepackage{todonotes}
\usepackage{multirow}
\usepackage{tikz}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{thmtools}		
\usepackage{mleftright}
\usepackage{stmaryrd}
\usepackage{nicefrac}

\theoremstyle{definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{observation}[theorem]{Observation}
\newtheorem{remark}[theorem]{Remark}

\usepackage{thm-restate}
\usepackage[mathic=true]{mathtools}
\usepackage{fixmath}
\usepackage{siunitx}
\usepackage{color}

\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\usepackage{enumitem}
\setlist[enumerate]{noitemsep, topsep=0.5\topsep}
\setlist[description]{noitemsep, topsep=0.5\topsep}
\setlist[itemize]{noitemsep, topsep=0.5\topsep}

\usepackage{setspace}
\usepackage[protrusion=true,expansion=false, activate={true,nocompatibility},final,kerning=true,spacing=true]{microtype}
\usepackage[]{microtype}
\usepackage{ellipsis}
\usepackage{xspace}
\usepackage{hfoldsty}

\usepackage{tcolorbox}
\usepackage{lmodern}

%\addtokomafont{disposition}{\rmfamily}
%\addtokomafont{descriptionlabel}{\rmfamily}

%\usepackage{newpxtext,newpxmath}
%\usepackage{classico}

%\usepackage[tt=false]{libertine}
%\usepackage[varqu]{zi4}
%\usepackage[libertine]{newtxmath}

\usepackage[
pdfa,
hidelinks,
pdftex, 
pdfdisplaydoctitle,
pdfpagelabels,
pdfauthor={},
pdftitle={},
pdfsubject={},
pdfkeywords={},
pdfproducer={Latex with the hyperref package},
pdfcreator={pdflatex}
]{hyperref}

% Let cleveref and thmtools work together
\makeatletter
\def\thmt@refnamewithcomma #1#2#3,#4,#5\@nil{%
	\@xa\def\csname\thmt@envname #1utorefname\endcsname{#3}%
	\ifcsname #2refname\endcsname
	\csname #2refname\expandafter\endcsname\expandafter{\thmt@envname}{#3}{#4}%
	\fi
}
\makeatother
\usepackage[capitalise,noabbrev]{cleveref}   
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\algdef{SE}{ParForAllLoop}{EndParForAllLoop}[1]{\textbf{parallel for}\(\mbox{#1}\) \textbf{do}}{\textbf{end}}

\newcommand{\new}[1]{\emph{#1}}

\DeclarePairedDelimiter{\norm}{\lVert}{\rVert}
\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

\newcommand{\cA}{\ensuremath{{\mathcal A}}\xspace}
\newcommand{\cB}{\ensuremath{{\mathcal B}}\xspace}
\newcommand{\cC}{\ensuremath{{\mathcal C}}\xspace}
\newcommand{\cD}{\ensuremath{{\mathcal D}}\xspace}
\newcommand{\cF}{\ensuremath{{\mathcal F}}\xspace}
\newcommand{\cH}{\ensuremath{{\mathcal H}}\xspace}
\newcommand{\cN}{\ensuremath{{\mathcal N}}\xspace}
\newcommand{\cM}{\ensuremath{{\mathcal M}}\xspace}

\newcommand{\cO}{\ensuremath{{\mathcal O}}\xspace}
\newcommand{\cI}{\ensuremath{{\mathcal I}}\xspace}
\newcommand{\cP}{\ensuremath{{\mathcal P}}\xspace}
\newcommand{\cR}{\ensuremath{{\mathcal R}}\xspace}
\newcommand{\cS}{\ensuremath{{\mathcal S}}\xspace}
\newcommand{\cU}{\ensuremath{{\mathcal U}}\xspace}
\newcommand{\cV}{\ensuremath{{\mathcal V}}\xspace}
\newcommand{\cPn}{\ensuremath{{\mathcal P}_n}\xspace}

\newcommand{\fA}{\ensuremath{\mathfrak{A}}\xspace}
\newcommand{\fB}{\ensuremath{\mathfrak{B}}\xspace}
\newcommand{\fC}{\ensuremath{\mathfrak{C}}\xspace}

\newcommand{\fa}{\ensuremath{\mathfrak{a}}\xspace}
\newcommand{\fb}{\ensuremath{\mathfrak{b}}\xspace}
\newcommand{\fc}{\ensuremath{\mathfrak{c}}\xspace}
\newcommand{\fd}{\ensuremath{\mathfrak{d}}\xspace}

\newcommand{\bA}{\ensuremath{{\bf A}}\xspace}
\newcommand{\bB}{\ensuremath{{\bf B}}\xspace}
\newcommand{\bK}{\ensuremath{{\bf K}}\xspace}
\newcommand{\bE}{\ensuremath{{\bf E}}\xspace}
\newcommand{\bN}{\ensuremath{{\bf N}}\xspace}
\newcommand{\bG}{\ensuremath{{\bf G}}\xspace}

\newcommand{\ba}{\ensuremath{{\bf a}}\xspace}
\newcommand{\bb}{\ensuremath{{\bf b}}\xspace}
\newcommand{\bc}{\ensuremath{{\bf c}}\xspace}

\newcommand{\bbE}{\ensuremath{\mathbb{E}}}
\newcommand{\bbR}{\ensuremath{\mathbb{R}}}
\newcommand{\bbQ}{\ensuremath{\mathbb{Q}}}
\newcommand{\bbP}{\ensuremath{\mathbb{P}}}
\newcommand{\bbZ}{\ensuremath{\mathbb{Z}}}
\newcommand{\bbN}{\ensuremath{\mathbb{N}}}
\newcommand{\bbNn}{\ensuremath{\mathbb{N}_0}}

\newcommand{\bbRnp}{\ensuremath{\bbR_{\geq 0}}}
\newcommand{\bbQnp}{\ensuremath{\bbQ_{\geq}}}
\newcommand{\bbZnp}{\ensuremath{\bbZ_{\geq}}}

\newcommand{\bbRsp}{\ensuremath{\bbR_>}}
\newcommand{\bbQsp}{\ensuremath{\bbQ_>}}
\newcommand{\bbZsp}{\ensuremath{\bbZ_>}}

\newcommand{\cp}{\textsf{P}\xspace}
\newcommand{\cnp}{\textsf{NP}\xspace}

\newcommand{\RR}{\mathbb{R}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\PP}{\mathbb{P}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\GG}{\mathbb{G}}
\newcommand{\GN}{\mathbb{G}_n}

\newcommand{\rb}{\right\}\xspace}
\newcommand{\lb}{\left\{\xspace}
\newcommand{\lbr}{\left(\xspace} 
\newcommand{\rbr}{\right)\xspace}
\newcommand{\ndelta}{\ensuremath{\overline{\delta}}}

\newcommand{\oms}{\{\!\!\{}
\newcommand{\cms}{\}\!\!\}}

\newcommand{\trans}{^\mathsf{T}}
\renewcommand{\vec}[1]{\mathbf{#1}}

\usepackage[auth-lg]{authblk}
\newcommand{\cm}[1]{{{\textcolor{blue}{\textbf{[CM:} {#1}\textbf{]}}}}}
\newcommand{\ebk}[1]{{{\textcolor{green}{\textbf{[EBK:} {#1}\textbf{]}}}}}
\renewcommand*{\Affilfont}{\normalsize\normalfont}
\renewcommand*{\Authfont}{\sffamily}

\recalctypearea

\begin{document}
\title{MIP-GNN: A data-driven tool for guiding combinatorial solvers}
\author[1]{Elias B.~Khalil}
\author[2]{Christopher Morris}

\affil[1]{CERC in Data Science for Real-Time Decision-Making, Polytechnique Montr{\'e}al}	
\affil[2]{Department of Mechanical \& Industrial Engineering, University of Toronto}
\date{\vspace{-30pt}}

\maketitle

\begin{abstract}
Write abstract. Theme: general data-driven tool for replacing heuristic components of MIP solvers.

\end{abstract}

\section{Introduction}
Write introduction, main points (MIP-GNN is a general purpose tool for guiding decision throughout the solving process of MIPs in a data-driven way):
\begin{itemize}
	\item MIPs solvers use many heuristics throughout solving process, need for data-driven heuristics that adapt to the problem distribution
	\item Graphs as a natural way to represent BIPs/ILPs/MIPs and other constraint convex optimization problems, graphs are a natural inductive bias
	\item Arguments of Fischetti 
\end{itemize}

\paragraph{Present work} Contribution.
\begin{itemize}
	\item General approach, many different applications within the MIP/B\&C solving framework, list examples
	\item Connection to MWU problem (theoretically principled, MWU can be recovered)
	\item Experimental evaluation on real-world instances, speed-up of $X$
\end{itemize}

\paragraph{Related work} Discuss related work.
\begin{itemize}
	\item Most important GNN papers,
	\item GNNs to solve MIPs/comb. optimization problems,
	\item Papers on SAT and CSP solving (Hsu, LeSong, Aachen, Dilkina, Khalil, \dots) 
\end{itemize}

\section{Preliminaries}

In the following, we fix notation and give a short introduction to GNNs, binary integer programs, and setup the learning program.

\subsection{Notation}

\cm{shorten}
A \new{graph} $G$ is a pair $(V,E)$ with a \emph{finite} set of
\new{vertices} $V$ and a set of \new{edges} $E \subseteq \{ \{u,v\}
\subseteq V \mid u \neq v \}$. We denote the set of vertices and the set
of edges of $G$ by $V(G)$ and $E(G)$, respectively. For ease of
notation, we denote the edge $\{u,v\}$ in $E(G)$ by $(u,v)$ or
$(v,u)$. In the case of \emph{directed graphs} $E \subseteq \{ (u,v)
\in V \times V \mid u \neq v \}$. A \new{labeled graph} $G$ is a triple
$(V,E,l)$ with a label function $l \colon V(G) \cup E(G) \to \Sigma$,
where $\Sigma$ is some finite alphabet. Then $l(v)$ is a
\new{label} of $v$ for $v$ in $V(G) \cup E(G)$. 
The \new{neighborhood} 
of $v$ in $V(G)$ is denoted by $\delta(v) = N(v) = \{ u \in V(G) \mid (v, u) \in E(G) \}$. 
Moreover, its complement $\ndelta(v) = \{ u \in V(G) \mid (v, u) \notin E(G) \}$. 
Let $S \subseteq
V(G)$ then $G[S] = (S,E_S)$ is the \new{subgraph induced} by $S$ with
$E_S = \{ (u,v) \in E(G) \mid u,v \in S \}$. A \new{tree} is a connected graph without
cycles. A \new{rooted tree} is a tree with a designated vertex called \new{root} in which the edges are directed in such a way that they point away from the root. \cm{biparite graph}
Let $p$ be a vertex in a directed tree then we call its out-neighbors \new{children} with parent $p$. 
\cm{Add matrix notation, all-row vectors}
We say that two graphs $G$ and $H$
are \new{isomorphic} if there exists an edge preserving bijection
$\varphi \colon V(G) \to V(H)$, i.e., $(u,v)$ is in $E(G)$ if and only if
$(\varphi(u),\varphi(v))$ is in $E(H)$. If $G$ and $H$ are isomorphic,
we write $G \simeq H$ and call $\varphi$ an \new{isomorphism} between
$G$ and $H$. Moreover, we call the equivalence classes induced by
$\simeq$ \emph{isomorphism types}, and denote the isomorphism type of $G$ by
$\tau_G$. In the case of labeled graphs, we additionally require that
$l(v) = l(\varphi(v))$ for $v$ in $V(G)$ and $l((u,v)) = l((\varphi(u), \varphi(v)))$ for $(u,v)$ in $E(G)$. 
Moreover, let $[n] = \{ 1, \dotsc, n \} \subset \NN$ for $n \geq 1$, and let $\{\!\!\{ \dots\}\!\!\}$ denote a multiset.

\subsection{Binary integer programs}\label{bip}

An \emph{instance} $I$ of binary integer program (BIP) is a $3$-tuple $(\vec{c}, \vec{A}, \vec{b})$, with a vector $\vec{c}$ in a matrix $\vec{A}$ in $\RR^{n \times m}$, and $\vec{b}$ in $\RR^{m}$. We interpret the former as a (linear) \new{objective} or \new{cost function}, and the latter two  are interpreted as a system of linear equations, i.e., $\vec{A} \vec{x} \geq \vec{b}$, which induces a set of \emph{feasible solutions} $F(I) = \{ \vec{x} \in \RR^n \mid \vec{A} \vec{x} \geq \vec{b}, \vec{x} \geq 0 \}$. We call each component of $\vec{x}$ a \new{variable}, and the set $\cV(I) = \{x_i \}_{i \in [n]}$ the (set of) variables.

The \new{optimal integral solution} $\vec{x}^*$ is equal to $\arg\max_{\vec{x} \in \{0,1\}^n} \{ \vec{c}\trans \vec{x} \mid \vec{A} \vec{x} \geq \vec{b}, \vec{x} \geq 0  \}$, i.e., we maximize the linear functional $\vec{c}$ over $F(I)_{0,1} = F(I) \cap \{ 0,1 \}^n$. The \emph{optimal solution} $\bar{\vec{x}}$ of the \new{relaxed BIP} is obtained by dropping the integrality contraints, i.e., $\vec{\bar{x}} = \arg\max_{\vec{x} \in [0,1]^n} \{ \vec{c}\trans \vec{x} \mid \vec{A} \vec{x} \geq \vec{b}, \vec{x} \geq 0 \}$. In other words, we maximize the linear functional $\vec{c}$ over $F(I)$.

\cm{State connection to comb. optimization}

\subsection{Graph neural networks}
Let $G$ be a labeled graph $(V,E,l)$ with an initial vertex coloring $f^{(0)} \colon V(G)\rightarrow \RR^{1\times d}$ that is \emph{consistent} with $l$. That is, each vertex $v$ is annotated with a feature $\vec{f}^{(0)}(v)$ in $\bbR^{1\times d}$ such that $\vec{f}^{(0)}(u) = \vec{f}^{(0)}(v)$ if and only if $l(u) = l(v)$.
Alternatively, $\vec{f}^{(0)}(v)$ can be an arbitrary  real-valued feature vector associated with $v$. A GNN architecture consists of a stack of neural network layers, where each layer aggregates local neighborhood information, i.e., features of neighbors, and then passes this aggregated information on to the next layer.  In each round or layer $t$ a new feature $\vec{f}^{(t)}(v)$ is computed as
\begin{equation}\label{eq:gnngeneral}
f^{\vec{W_2}}_{\textsc{Up}}\Big(\vec{f}^{(t-1)}(v) ,f^{\vec{W_1}}_{\textsc{Agg}}\big(\oms  \vec{f}^{(t-1)}(w) \mid  w \in N(v) \cms \big)\Big),
\end{equation}
where $f^{\vec{W_1}}_{\text{aggr}}$ aggregates over the set of neighborhood features and $f^{\vec{W_2}}_{\text{merge}}$ merges the vertex's representations from step $(t-1)$ with the computed neighborhood features.
Both $f^{\vec{W_1}}_{\text{aggr}}$ and $f^{\vec{W_2}}_{\text{merge}}$ may be arbitrary differentiable, (permutation-invariant) functions (e.g., neural networks), and $\vec{W_1}$ and $\vec{W_2}$, respectively, denote sets of parameters.

\subsection{Setup of the learning problem}
Let $\cC$ be the set of all instances of a combinatorial optimization problem that can be formulated as a BIP. Let $I$ be an instance in $\cC$, then let $X^*_{\varepsilon}(I) = \{ \vec{x} \in F_{0,1}(I) \mid \vec{c}\trans\vec{x}^* - \vec{c}\trans\vec{x} \leq \varepsilon \}$ be a set of integral solutions that are \glqq close\grqq{}  to the optimum of the instance $I$. That is, their solution value is equal to the optimal value up to a prespecified $\varepsilon$. The \new{variable bias} $\vec{\bar{b}}(I)$ of $I$ with regard to $X^*_{\varepsilon}(I)$  then is the component-wise average over all elements, i.e., the variable bias $\vec{\bar{b}}(I) = \nicefrac{1}{|X^*_{\varepsilon}|}\sum_{\vec{x} \in X^*_{\varepsilon}(I)} \vec{x}$ in $\bbR^n$.

The aim here is to devise a neural architecture and train a corresponding model in  a supervised fashion to predict the variable bias $\vec{\bar{b}}(I)$ for unseen instances. Hence, let $D$ be a distribution over $\cC$ and let $S$ be a finite subset (training set) sampled uniformly and at random from $D$. We want to learn a function $f_{\theta} \colon \cV(I) \to \RR$, where $\theta$ represents a set of parameters in the set $\Theta$, that predicts the variable biases of out-of-sample instances. Hence, we optimize the empirical error
\begin{equation*}
\min_{\theta \in \Theta} \nicefrac{1}{|S|}\sum_{I \in S} \ell(f_{\theta}(\cV(I)),\vec{\bar{b}}(I)),
\end{equation*}
with some loss function $\ell \colon \bbR^n \times \bbR^n \to \bbR$ over the set of parameters $\Theta$.

\cm{Combination of GNN and MWU }

\subsection{Multiplicative weights update algorithm for linear programs}

The \new{multiplicative weights update algorihm} (MWU) is a framework to solve various computational problems that can be solved by iterativly adapting a discrete probability distribution over a certain set~\cite{Aro+2012}. Here, we describe the variant of the MWU to determine the feasibility of a system of a system of linear equations.

Given a system of linear equations $\vec{A} \vec{x} \geq \vec{b}$, see~\cref{bip}, the MWU tries to determine if the above system is feasible up to a prespecified $\varepsilon > 0$. That is, it determines if there exists $\vec{\bar{x}}$ such that 
\begin{equation}\label{epsfeas}
\vec{A}_i \vec{\bar{x}} \geq b_i - \varepsilon,
\end{equation}
for $i$ in $[m]$.\cm{say sth. about optimal solution, give intution of the MWU, discrete prob., oracle for LP, Farkas' lemma.}

\begin{algorithm}[H]\mbox{\hfill}
\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
\begin{algorithmic}[1]
	\State Initialize constraint weights $w_i \leftarrow 1$ for $i$ in $[m]$ 
	\State Set $T$ to according~\cref{mwubound}
	\For{$t \text{ in } [T]$}
	\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)} $  for $i$ in $[m]$, where $\Phi(t) = \sum_{i \in [m]} w_i$
	\State Call oracle: $\vec{x}(t) \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$ if $
	\vec{x}(t) = \emptyset$ \Return  \texttt{non-feasible}
	\State Compute error signal $\vec{m}$ with
	\begin{equation*}
		m_i \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_i\trans \vec{x}(t) - b_i)   
	\end{equation*}
	\State Perform gradient descent  by $w_i(t+1) \leftarrow ( 1 -  \eta m_i) w_i(t) $ 
	\EndFor
	\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
\end{algorithmic}
\caption{MWU for the LP feasibility problem.}
\label{alg:as}
\end{algorithm}

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:} $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
	\begin{algorithmic}[1]
		\State Initialize constraint weights $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
		\State Set $T$ to according~\cref{mwubound}
		\For{$t \text{ in } [T]$}
		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable 
		\Statex
		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
		\Statex
		\State Send $\vec{x}_i$ to each adjacent constraint, compute error signal $\vec{m}_i$ for each constraint $\vec{c}_j$
		\begin{equation*}
		\vec{m}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j   
		\end{equation*}
		\State Perform gradient descent  by $\vec{w}_i(t+1) \leftarrow ( 1 -  \eta \vec{m}_i) \vec{w}_i(t) $ 
		\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)}$ for each constraint node, where $\Phi(t) = \sum_{i \in [m]} w_i$

		\EndFor
		\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
	\end{algorithmic}
	\caption{MWU (Message Passing version) for the LP feasibility problem.}
	\label{alg:as}
\end{algorithm}

We get the following bound of the running time.
\begin{theorem}[E.g., \cite{Aro+2012}]
	\cm{fill in details}
	\begin{equation}\label{mwubound}
		T = \left\lceil \frac{8 l \rho \ln(m)}{\varepsilon^2} \right\rceil 
	\end{equation}
\end{theorem}

\section{The MIP-GNN architecture}

Let $I = (\vec{c}, \vec{A}, \vec{b})$ be a BIP. The bipartite graph $B(I)$ of $I$ is three tuple $(V(I),C(I),E(I))$. Here, the vertex set $V(I) = \{ v_i \mid x_i \in \cV(I) \}$ represent the variables, and the set $C(I) = \{ c_i \mid i \in [m]  \}$ represent the constraints of $I$. The edge set $E(I) = \{ \{ v_i,c_j \} \mid A_{ij} \neq 0 \}$. Further, we define (node) label function $c\colon V(I) \to \bbR$, defined by $v_i \mapsto c_i$, and the (edge) label function $a \colon E(I) \to \bbR$, defined by  $(v_i,v_j) \mapsto A_{ij}$.
\cm{add more label functions }

Intuitively, each round $t \geq 0$ of message-passing consists of two \emph{passes}, the \new{variable to constraint} $f^{(t)}_{\text{V$\to$C}}\colon C(I) \to \RR^{1\times d}$ pass, followed by the \text{constraint to variable} pass $f^{(t)}_{\text{C$\to$V}}\colon V(I) \to \RR^{1\times d}$. 
\cm{Say sth. about the initialiazation, gaussian?}
\cm{Say sth. about cost }
In the following, we gives details about the two passes.

\paragraph{Variable to constraints.}

\paragraph{Constraint to variable:} sdfdsf

\begin{algorithm}[H]\mbox{\hfill}
	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$ 
	\begin{algorithmic}[1]
		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$, and $\boldsymbol{\theta}$
		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
		\Statex
		\For{$e \text{ in } [E]$}
		\State \cm{Make p a parameter?}
		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with bias  $\vec{\bar{b}}$ uniformly and at random from $\cS$ \cm{define Ib}
		\For{$t \text{ in } [T]$}
		\State $\vec{v}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{v}^{(t-1)}_i, \vec{c}_j, \vec{A}_{ij}, \vec{p}_j \right)\hspace{-3pt} \colon j \in N(\vec{v}_i) \right\} \hspace{-5pt} \right\} \right)\quad$		 $\vec{x}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}}   \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ %\cm{Oracle?}
		%\Statex
		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow \mathbf{f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}_i, \vec{x}_i, \vec{A}_{ij}, \vec{b}_j \right)\hspace{-3pt} \colon i \in N(\vec{c}_j) \right\} \hspace{-5pt} \right\} \right)$
		\State $\vec{e}_j^{(t)} \leftarrow \nicefrac{1}{\rho}\! \sum_{i \in N(j)} \vec{A}_{ji} \vec{x}_i^{(t)} - \vec{b}_j$
		%\Statex
		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}_j) \vec{w}_j^{(t)} $ 
		\State $\vec{p}_j \leftarrow \frac{w_j^{(t)}}{\Phi(t)} $, where $\Phi(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
		\EndFor
		\State g
		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
		\State Gradient descent on L
		\EndFor
		\State \Return $\boldsymbol{\theta}$

	\end{algorithmic}
	\caption{Data-driven MWU for variable bias prediction.}
	\label{alg:as2}
\end{algorithm}
\cm{overloading of c}

\subsection{Unsupervised setting}

random matrices, recover MWU, also test in experiments

\subsection{Discussion: Road blocks and the road ahead}

discuss limitation of GNNs approaches, unsupervised approaches

discuss problems of generating labeled training data

\section{Experimental evaluation}

Our intention here is to investigate the benefits of ... the compared to...
More precisely, we address the following questions:\\
\begin{description}
	\item[Q1] description
	\item[Q2] description
	\item[Q3] description
\end{description}

\section{Conclusion}
Write conclusion.			
\bibliography{bibliography}
\bibliographystyle{plainnat}

\end{document}

### 2020-08-05 paper/main.tex
Startet paper.

@@
 \begin{algorithm}[H]\mbox{\hfill}
-\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
+\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
 \textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
 \begin{algorithmic}[1]
-	\State Initialize constraint weights $w_i \leftarrow 1$ for $i$ in $[m]$ 
+	\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
+	\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
 	\State Set $T$ to according~\cref{mwubound}
 	\For{$t \text{ in } [T]$}
-	\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)} $  for $i$ in $[m]$, where $\Phi(t) = \sum_{i \in [m]} w_i$
-	\State Call oracle: $\vec{x}(t) \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$ if $
-	\vec{x}(t) = \emptyset$ \Return  \texttt{non-feasible}
-	\State Compute error signal $\vec{m}$ with
+
+	\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
+	\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
+	\State Compute error signal $\vec{e}$, where
 	\begin{equation*}
-		m_i \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_i\trans \vec{x}(t) - b_i)   
+		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
 	\end{equation*}
-	\State Perform gradient descent  by $w_i(t+1) \leftarrow ( 1 -  \eta m_i) w_i(t) $ 
+	\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
+	\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
+	\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
 	\EndFor
-	\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
+	\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
 \end{algorithmic}
@@
 \begin{algorithm}[H]\mbox{\hfill}
-	\\\textbf{Input:} $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$, failure probability $\delta$. \\
+	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
 	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
 	\begin{algorithmic}[1]
-		\State Initialize constraint weights $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
+		\State Initialize weights $\vec{w}_j \leftarrow 1$ for each constraint node
+		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for each constraint node
 		\State Set $T$ to according~\cref{mwubound}
@@
 		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable 
-		\Statex
 		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
-		\Statex
-		\State Send $\vec{x}_i$ to each adjacent constraint, compute error signal $\vec{m}_i$ for each constraint $\vec{c}_j$
+		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
 		\begin{equation*}
-		\vec{m}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j   
+		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
 		\end{equation*}
-		\State Perform gradient descent  by $\vec{w}_i(t+1) \leftarrow ( 1 -  \eta \vec{m}_i) \vec{w}_i(t) $ 
-		\State Normalize weights $p_j \leftarrow \frac{w_j(t)}{\Phi(t)}$ for each constraint node, where $\Phi(t) = \sum_{i \in [m]} w_i$
-
+		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
+		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
+		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
 		\EndFor
-		\State \Return $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
+		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T}$
 	\end{algorithmic}
-	\caption{MWU (Message Passing version) for the LP feasibility problem.}
+	\caption{MWU (Message passing version) for the LP feasibility problem.}
 	\label{alg:as}
@@
 		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
-		\State Gradient descent on L
+		\State Gradient descent on $L$
 		\EndFor
@@
 \cm{overloading of c}
-
+\cm{how to incoperate data information}
 \subsection{Unsupervised setting}
@@
 
-discuss limitation of GNNs approaches, unsupervised approaches
+discuss limitation of GNNs approaches (bipartite GNN), unsupervised approaches
 

### 2020-08-05 paper/main.tex
MC.

@@
 	\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
-\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
+	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
 	\begin{algorithmic}[1]
@@
 		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
-	\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
+		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
 		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
@@
 \end{algorithm}
-
+Same algorithm as above interpreted as a message passing algorithm:
 \begin{algorithm}[H]\mbox{\hfill}
 	\\\textbf{Input:} Biparite constraint graph $B(I)$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
-	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}
+	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
 	\begin{algorithmic}[1]
@@
 		\For{$t \text{ in } [T]$}
-		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable 
+		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable \Comment{Constraint to variable pass}
+		\Statex
 		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
-		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
+		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$\Comment{Variable to constraint pass}
 		\begin{equation*}
-		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
+		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
 		\end{equation*}
 		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
-		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\Phi} $  for $i$ in $[m]$, where $\Phi = \sum_{i \in [m]} \vec{w}_i$
+		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
 		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
@@
 \begin{algorithm}[H]\mbox{\hfill}
-	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
-	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$ 
+	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of epochs $E$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
+	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
 	\begin{algorithmic}[1]
-		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$, and $\boldsymbol{\theta}$
+		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$
+		\State Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}})$
 		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
+		\For{$e \text{ in } [E]$}
+		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with variable bias $\vec{\bar{b}}$ uniformly and at random from $\cS$, inducing the bipartite graph $B(I)$
+		\For{$t \text{ in } [T]$}
+		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$
+		\Comment{Constraint to variable pass}
+		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ \Comment{Generate variable assigment}
 		\Statex
-		\For{$e \text{ in } [E]$}
-		\State \cm{Make p a parameter?}
-		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with bias  $\vec{\bar{b}}$ uniformly and at random from $\cS$ \cm{define Ib}
-		\For{$t \text{ in } [T]$}
-		\State $\vec{v}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{v}^{(t-1)}_i, \vec{c}_j, \vec{A}_{ij}, \vec{p}_j \right)\hspace{-3pt} \colon j \in N(\vec{v}_i) \right\} \hspace{-5pt} \right\} \right)\quad$		 $\vec{x}_i^{(t)} \leftarrow \mathbf{f}^{(t)}_{\text{V}}   \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ %\cm{Oracle?}
+		\Statex
+		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$ 		\Comment{Variable to constraint pass}
+		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j$
 		%\Statex
-		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow \mathbf{f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-5pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}_i, \vec{x}_i, \vec{A}_{ij}, \vec{b}_j \right)\hspace{-3pt} \colon i \in N(\vec{c}_j) \right\} \hspace{-5pt} \right\} \right)$
-		\State $\vec{e}_j^{(t)} \leftarrow \nicefrac{1}{\rho}\! \sum_{i \in N(j)} \vec{A}_{ji} \vec{x}_i^{(t)} - \vec{b}_j$
-		%\Statex
-		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}_j) \vec{w}_j^{(t)} $ 
-		\State $\vec{p}_j \leftarrow \frac{w_j^{(t)}}{\Phi(t)} $, where $\Phi(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
+		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}^{(t)}_j) \vec{w}_j^{(t-1)} $ 
+		\State $\vec{p}_j \leftarrow \nicefrac{w_j^{(t)}}{\boldsymbol{\Gamma}(t)} $, where $\boldsymbol{\Gamma}(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
+		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
 		\EndFor
-		\State g
 		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
 		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
-		\State Gradient descent on $L$
+		\State Gradient descent on $\nicefrac{1}{T} L$ with regard to $\boldsymbol{\theta}$
 		\EndFor
@@
 \end{algorithm}
+
 \cm{overloading of c}

### 2020-08-06 paper/main.tex
Rest of experiments.

@@
 		\For{$t \text{ in } [T]$}
-		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable \Comment{Constraint to variable pass}
+		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable
 		\Statex
 		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
-		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$\Comment{Variable to constraint pass}
+		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
 		\begin{equation*}
@@
 		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$
-		\Comment{Constraint to variable pass}
-		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ \Comment{Generate variable assigment}
+
+		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ 
 		\Statex
 		\Statex
-		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$ 		\Comment{Variable to constraint pass}
+		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$
 		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j$

### 2020-08-18 paper/main.tex
Started implementing new model.

@@
 \renewcommand{\vec}[1]{\mathbf{#1}}
+%\renewcommand{\vec}[1]{#1}
 
@@
 	\item Most important GNN papers, 
-	\item GNNs to solve MIPs/comb. optimization problems,
-	\item Papers on SAT and CSP solving (Hsu, LeSong, Aachen, Dilkina, Khalil, \dots) 
+	\item GNNs to solve MIPs/comb. optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gasse+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: 
+	\item Papers on SAT and CSP solving (Hsu, LeSong, Aachen, Loukas \dots) \cite{Sel+2019}
 \end{itemize}
+
+GNN: Recently, graph neural networks (GNNs)~\cite{Gil+2017,Sca+2009} emerged as a flexible framework for machine learning on graphs and relational data.
+Notable instances of this architecture include, e.g.,~\cite{Duv+2015,Ham+2017,Vel+2018}, and the spectral approaches proposed in, e.g.,~\cite{Bru+2014,Def+2015,Kip+2017,Mon+2017}---all of which descend from early work in~\cite{Kir+1995,Mer+2005,Spe+1997,Sca+2009}.
+A survey of recent advancements in GNN techniques can be found, e.g., in~\cite{Cha+2020,Wu+2019,Zho+2018}.
+The limits of GNNs have been studied in~\cite{Bar+2020,Che+2019,Mae+2019,Mar+2019,Mor+2019,Xu+2018b}.
 
@@
 \cm{State connection to comb. optimization}
+\cm{Background on bb, branching etc}
 
@@
 
-\begin{algorithm}[H]\mbox{\hfill}
-	\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
-	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
-	\begin{algorithmic}[1]
-		\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
-		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
-		\State Set $T$ to according~\cref{mwubound}
-		\For{$t \text{ in } [T]$}
-
-		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
-		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
-		\State Compute error signal $\vec{e}$, where
-		\begin{equation*}
-		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
-		\end{equation*}
-		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
-		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
-		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
-		\EndFor
-		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
-	\end{algorithmic}
-	\caption{MWU for the LP feasibility problem.}
-	\label{alg:as}
-\end{algorithm}
+%\begin{algorithm}[H]\mbox{\hfill}
+%	\\\textbf{Input:} System of linear equations $\vec{A} \vec{x} \geq \vec{b}$, $\varepsilon > 0$,  stepsize $\eta > 0$, scaling constant $\rho$. \\
+%	\textbf{Output:} $\vec{\bar{x}}$ satisfying~\cref{epsfeas} or \texttt{non-feasible}.
+%	\begin{algorithmic}[1]
+%		\State Initialize constraint weights $\vec{w}_i \leftarrow 1$ for $i$ in $[m]$ 
+%		\State Initialize probabilities $\vec{p}_j \leftarrow \nicefrac{1}{m}$ for $i$ in $[m]$ 
+%		\State Set $T$ to according~\cref{mwubound}
+%		\For{$t \text{ in } [T]$}
+%		
+%		\State Call oracle: $\vec{x} \leftarrow \cO(\vec{p}\trans \vec{A} \vec{x} \geq \vec{p}\trans \vec{b})$, \textbf{if} $
+%		\vec{x} = \emptyset$ \Return  \texttt{non-feasible}
+%		\State Compute error signal $\vec{e}$, where
+%		\begin{equation*}
+%		\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,(\vec{A}_j\trans \vec{x}(t) - \vec{b}_j)   
+%		\end{equation*}
+%		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
+%		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
+%		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
+%		\EndFor
+%		\State \Return Average over solution $ \nicefrac{\vec{\bar{x}}}{T} $
+%	\end{algorithmic}
+%	\caption{MWU for the LP feasibility problem.}
+%	\label{alg:as}
+%\end{algorithm}
+\cm{exploration/exploitation $\eta$}
 Same algorithm as above interpreted as a message passing algorithm:
@@
 		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$
-		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j$
+		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j$
 		%\Statex
@@
 \cm{how to incoperate data information}
+
+\begin{algorithm}[H]\mbox{\hfill}
+	\\\textbf{Input:}  Training set $S$, number of epochs $E$, number of layers $T$, stepsize $\eta > 0$.  \\
+	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
+	\begin{algorithmic}[1]
+		\State Initialize $\vec{v}^{(0)}$ and $\vec{c}^{(0)}$
+
+		\State Initialize $\vec{p}_i^{(0)} \leftarrow 1/m$
+		\For{$e \text{ in } [E]$}
+		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ from $U(S)$ 
+		\For{$t \text{ in } [T]$}
+		\State $\vec{V}_j^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$
+
+		\State $\vec{X}_j^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \big(\vec{V}_i^{(t-1)} \big)$ for all $j$ in $[n]$ 
+		\Statex
+		\Statex
+		\State $\vec{C}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_j, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_j \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$
+		%\State $\vec{e}_j^{(t)} \leftarrow \sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i - \vec{b}_j$
+		%\Statex
+		\State $\vec{p}_{j}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_{\text{P}}(\vec{e}^{(t)}))_{j}$
+		\EndFor
+		\State $\bar{\vec{x}} \leftarrow f(\mathbin\Vert_{t \in [T]} \vec{x}^{(t)})$
+		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
+		\State Gradient descent on $L$ with regard to $\boldsymbol{\theta}$
+		\EndFor
+		\State \Return $\boldsymbol{\theta}$
+
+	\end{algorithmic}
+	\caption{MIP-GNN for variable bias prediction.}
+	\label{alg:as2}
+\end{algorithm}
+
+Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}}, \boldsymbol{\theta}_{\text{P}})$
+
+\subsection{Connnection to boosting}
+
+joint MWU and boosting
+
 \subsection{Unsupervised setting}

### 2020-08-18 gnn_models/classification_old/mip_alternating_arch_class.py

@@ -36,14 +36,18 @@ class CONS_TO_VAR(MessagePassing):
         return self.propagate(hidden_to_var=hidden_to_var, x=x, edge_index=edge_index, size=size, old_vars=old_vars,
                               asums=asums, edge_feature=edge_feature, norm=norm)
 
+    # TODO: x_j: constraint embeddings and x_i are variable embedding (target):
     def message(self, hidden_to_var, x_j, x_i, edge_index_j, edge_feature, norm, asums_j):
         # Get coefficients of variable in constraint.
         c = edge_feature[edge_index_j]
         # Get violation of contraint.
         violation = x_j[:, -1]
+
+        # Map variable to scalar (assigment of variable)
+        # TODO: Weird.
         violation = hidden_to_var(x_i).view(-1) * violation * c.view(-1)
-        # TODO: FIX numerical problems here
-        #violation = c.view(-1) / (asums_j) * hidden_to_var(x_i).view(-1) * violation
+        # TODO: Fix numerical problems here.
+        # violation = c.view(-1) / (asums_j) * hidden_to_var(x_i).view(-1) * violation
 
         # TODO: Scale by coefficient?
         out = self.mlp_cons(c * x_j)
@@ -94,6 +98,7 @@ class VARS_TO_CON(MessagePassing):
                               edge_feature=edge_feature, rhs=rhs,
                               norm=norm)
 
+    # TODO: x_j: var. embeddings and x_i are constraint embedding (target):
     def message(self, hidden_to_var, x_j, x_i, edge_index_j, edge_feature, norm):
         c = edge_feature[edge_index_j]
         # Compute variable assignment.
@@ -219,6 +224,10 @@ class Net(torch.nn.Module):
                                    data.edge_features_con, data.asums,
                                    (data.num_nodes_con, data.num_nodes_var)))
         else:
+            cons.append(
+                self.v2c_1(self.hidden_to_var_1, (v, c), c, data.edge_index_var, data.edge_features_var, data.rhs,
+                           (data.num_nodes_var.sum(), data.num_nodes_con.sum())))
+
             vars.append(
                 self.c2v_1(self.hidden_to_var_1, (cons[-1], v), v, data.edge_index_con, data.edge_features_con,
                            data.asums, (data.num_nodes_con.sum(), data.num_nodes_var.sum())))

### 2020-08-18 gnn_models/classification_old/train_model_bipartite_class.py

@@ -45,6 +45,7 @@ class GISR(InMemoryDataset):
         path = '../gisp_generator/DATA/er_200_SET2_1k/'
         total = len(os.listdir(path))
 
+        # Iterate over instance file and create data objects.
         for num, filename in enumerate(os.listdir(path)):
             print(filename, num, total)
 
@@ -64,7 +65,7 @@ class GISR(InMemoryDataset):
             var_i = 0
             # Number of constraints.
             con_i = 0
-            # Targets
+            # Targets.
             y = []
             # Features for variable nodes.
             var_feat = []
@@ -80,16 +81,20 @@ class GISR(InMemoryDataset):
                     var_node[i] = var_i
                     var_i += 1
 
+                    # TODO: Think of a better way to do this.
                     if (node_data['bias'] < 0.05):
                         y.append(0)
                     else:
                         y.append(1)
+
                     # TODO: Scaling meaingful?
                     var_feat.append([node_data['objcoeff'] / 100.0, graph.degree[i]])
 
                 # Node is constraint.
                 else:
                     a = []
+
+                    # TODO: Check this, seems wrong.
                     for e in graph.edges(node, data=True):
                         a.append(graph[e[0]][e[1]]['coeff'])
                     a_sum.append(sum(a))
@@ -108,8 +113,11 @@ class GISR(InMemoryDataset):
             # Edge list for con->var graphs.
             edge_list_con = []
 
+            # Create sparse adjacency matrices for both sides of the biparitite graphs.
             edge_features_var = []
             edge_features_con = []
+
+            # TODO: Check if edges exists twice.
             for i, (s, t, edge_data) in enumerate(graph.edges(data=True)):
                 # Source node is con, target node is var.
                 if graph.nodes[s]['bipartite'] == 1:
@@ -122,6 +130,7 @@ class GISR(InMemoryDataset):
             edge_index_var = torch.tensor(edge_list_var).t().contiguous()
             edge_index_con = torch.tensor(edge_list_con).t().contiguous()
 
+            # Create data object.
             data.edge_index_var = edge_index_var
             data.edge_index_con = edge_index_con
             data.y = torch.from_numpy(np.array(y)).to(torch.long)
[…]

### 2020-08-18 gnn_models/mip_bipartite_class.py

@@ -1,0 +1,273 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+from sklearn.model_selection import train_test_split
+
+import torch
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+
+
+# Preprocessing to create Torch dataset.
+class GraphDataset(InMemoryDataset):
+
+    def __init__(self, root, data_path, bias_threshold, transform=None, pre_transform=None,
+                 pre_filter=None):
+        super(GraphDataset, self).__init__(root, transform, pre_transform, pre_filter)
+        self.data, self.slices = torch.load(self.processed_paths[0])
+        self.data_path = data_path
+        self.bias_threshold = bias_threshold
+
+
+
+    @property
+    def raw_file_names(self):
+        return "SET2_bi_class"
+
+    @property
+    def processed_file_names(self):
+        return "SET2_bi_class"
+
+    def download(self):
+        pass
+
+    def process(self):
+        print("Preprocessing.")
+
+        data_list = []
+
+        path = data_path
+        num_graphs = len(os.listdir(path))
+
+        # Iterate over instance files and create data objects.
+        for num, filename in enumerate(os.listdir(path)):
+            print(filename, num, num_graphs)
+
+            # Get graph.
+            graph = nx.read_gpickle(path + filename)
+
+            # Make graph directed.
+            graph = nx.convert_node_labels_to_integers(graph)
+            graph = graph.to_directed() if not nx.is_directed(graph) else graph
+            data = Data()
+
+            #  Maps networkx ids to new variable node ids.
+            node_to_varnode = {}
+            #  Maps networkx ids to new constraint node ids.
+            node_to_connode = {}
+
+            # Number of variables.
+            num_nodes_var = 0
+            # Number of constraints.
+            num_nodes_con = 0
+            # Targets (classes).
+            y = []
+            # Features for variable nodes.
+            feat_var = []
+            # Feature for constraints nodes.
+            feat_con = []
+            # Right-hand sides of equations.
+            feat_rhs = []
+
+            # Iterate over nodes, and collect features.
[…]

### 2020-08-18 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -10,22 +10,107 @@ import numpy as np
 import networkx as nx
 from sklearn.model_selection import train_test_split
 
-import torch
 from torch_geometric.data import (InMemoryDataset, Data)
 from torch_geometric.data import DataLoader
 
+import torch
+import torch.nn.functional as F
+from torch.nn import BatchNorm1d as BN
+from torch.nn import Sequential, Linear, ReLU
+from torch_geometric.nn import MessagePassing
+from torch_geometric.nn.inits import reset
+
+
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+
+class SimpleBipartiteLayer(MessagePassing):
+    def __init__(self, edge_dim, dim_init, dim):
+        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        self.edge_encoder = Sequential(Linear(edge_dim, dim_init), ReLU(), Linear(dim_init, dim_init), ReLU(),
+                                       BN(dim_init))
+        self.mlp = Sequential(Linear(dim_init, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
+
+    def forward(self, x, edge_index, edge_attr, size):
+        edge_embedding = self.edge_encoder(edge_attr)
+
+        print(x.size(), edge_index.size(), edge_attr.size())
+        print(size)
+
+        tmp = self.propagate(edge_index, x=x, edge_attr=edge_embedding, size=size)
+        print(tmp)
+        exit()
+
+        out = self.mlp((1 + self.eps) * x + tmp)
+
+
+        return out
+
+    def message(self, x_j, edge_attr):
+        return F.relu(x_j + edge_attr)
+
+    def update(self, aggr_out):
+        return aggr_out
+
+    def reset_parameters(self):
+        reset(self.edge_encoder)
+        reset(self.mlp)
+        self.eps.data.fill_(self.initial_eps)
+
+
+class SimpleNet(torch.nn.Module):
+    def __init__(self, hidden):
+        super(SimpleNet, self).__init__()
+        self.var_con_1 = SimpleBipartiteLayer(1, 2, hidden)
+        self.con_var_1 = SimpleBipartiteLayer(1, 2, hidden)
+        self.var_con_2 = SimpleBipartiteLayer(1, 2, hidden)
+
[…]

### 2020-08-19 paper/main.tex
Started implementing new model.
Cont. implementing new model.

@@
 \begin{itemize}
-	\item Most important GNN papers, 
-	\item GNNs to solve MIPs/comb. optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gasse+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: 
+	\item GNNs to solve MIPs/comb.
+optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gasse+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},
+
 	\item Papers on SAT and CSP solving (Hsu, LeSong, Aachen, Loukas \dots) \cite{Sel+2019}
@@
 
-\begin{algorithm}[H]\mbox{\hfill}
-	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of epochs $E$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
-	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
-	\begin{algorithmic}[1]
-		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$
-		\State Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}})$
-		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
-		\For{$e \text{ in } [E]$}
-		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with variable bias $\vec{\bar{b}}$ uniformly and at random from $\cS$, inducing the bipartite graph $B(I)$
-		\For{$t \text{ in } [T]$}
-		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$
-
-		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ 
-		\Statex
-		\Statex
-		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$
-		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j$
-		%\Statex
-		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}^{(t)}_j) \vec{w}_j^{(t-1)} $ 
-		\State $\vec{p}_j \leftarrow \nicefrac{w_j^{(t)}}{\boldsymbol{\Gamma}(t)} $, where $\boldsymbol{\Gamma}(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
-		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
-		\EndFor
-		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
-		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
-		\State Gradient descent on $\nicefrac{1}{T} L$ with regard to $\boldsymbol{\theta}$
-		\EndFor
-		\State \Return $\boldsymbol{\theta}$
-
-	\end{algorithmic}
-	\caption{Data-driven MWU for variable bias prediction.}
-	\label{alg:as2}
-\end{algorithm}
+%
+%\begin{algorithm}[H]\mbox{\hfill}
+%	\\\textbf{Input:}  Training set $\cS$, $\varepsilon > 0$, number of epochs $E$, number of rounds $T$, stepsize $\eta > 0$, scaling constant $\rho$.  \\
+%	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
+%	\begin{algorithmic}[1]
+%		\State Initialize $\vec{v}_i^{(0)}$, $\vec{c}_i^{(0)}$
+%		\State Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}})$
+%		\State Set weights $\vec{w}_j^{(0)} \leftarrow 1$, $\vec{p}_j^{(0)} \leftarrow \nicefrac{1}{m}$ for $j$ in $[m]$
+%		\For{$e \text{ in } [E]$}
+%		\State Sample $I = (\vec{c}, \vec{A}, \vec{b})$ with variable bias $\vec{\bar{b}}$ uniformly and at random from $\cS$, inducing the bipartite graph $B(I)$
+%		\For{$t \text{ in } [T]$}
+%		\State $\vec{v}_i^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{v}^{(t-1)}_i, \vec{c}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ji} \big)\hspace{-1pt} \colon c_j \in N(v_i) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[n]$
+%		
+%		\State $\vec{x}_i^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \left(\vec{v}_i^{(t-1)} \right)$ for all $i$ in $[n]$ 
+%		\Statex
+%		\Statex
+%		\State $\vec{c}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \left( \left\{ \hspace{-4.4pt} \left\{ \left( \vec{c}^{(t-1)}_j, \vec{v}^{(t)}_i, \vec{x}^{(t)}_i, \vec{A}_{ji}, \vec{b}_j \right)\hspace{-2pt} \colon i \in N(c_j) \right\} \hspace{-4.4pt} \right\} \right)$ for all $j$ in $[m]$
+%		\State $\vec{e}_j^{(t)} \, \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i \Big) - \vec{b}_j$
+%		%\Statex
+%		\State $\vec{w}_j^{(t)} \leftarrow ( 1 -  \eta \vec{e}^{(t)}_j) \vec{w}_j^{(t-1)} $ 
+%		\State $\vec{p}_j \leftarrow \nicefrac{w_j^{(t)}}{\boldsymbol{\Gamma}(t)} $, where $\boldsymbol{\Gamma}(t) = \sum_{j \in [m]} \vec{w}^{(t)}_j$
+%		\State Update solution $\vec{\bar{x}} \leftarrow \vec{\bar{x}} + \vec{x}$
+%		\EndFor
+%		\State $\vec{\bar{x}} \leftarrow \nicefrac{1}{T} \sum_{t \in [T]} \vec{x}(t) $
+%		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
+%		\State Gradient descent on $\nicefrac{1}{T} L$ with regard to $\boldsymbol{\theta}$
+%		\EndFor
+%		\State \Return $\boldsymbol{\theta}$
+%		
+%	\end{algorithmic}
+%	\caption{Data-driven MWU for variable bias prediction.}
+%	\label{alg:as2}
+%\end{algorithm}
 
@@
 \begin{algorithm}[H]\mbox{\hfill}
-	\\\textbf{Input:}  Training set $S$, number of epochs $E$, number of layers $T$, stepsize $\eta > 0$.  \\
+	\\\textbf{Input:}  Training set $S$, number of epochs $E$, number of layers $T$.  \\
 	\textbf{Output:} A trained model $f_{\boldsymbol{\theta}} \colon \cI \to [0,1]^n$.
 	\begin{algorithmic}[1]
-		\State Initialize $\vec{v}^{(0)}$ and $\vec{c}^{(0)}$
-
-		\State Initialize $\vec{p}_i^{(0)} \leftarrow 1/m$
+		\State Initialize $\vec{v}^{(0)}$, $\vec{c}^{(0)}$, and $\vec{p}_i^{(0)}$
+		\Statex
 		\For{$e \text{ in } [E]$}
@@
 		\For{$t \text{ in } [T]$}
-		\State $\vec{V}_j^{(t)} \leftarrow {f}^{(t)}_{\text{V}} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$
-
-		\State $\vec{X}_j^{(t)} \leftarrow {f}^{(t)}_{\text{X}} \hspace{-2pt} \big(\vec{V}_i^{(t-1)} \big)$ for all $j$ in $[n]$ 
+		%\State \textit{Compute variable embedding:}
+		\State $\vec{V}_j^{(t)} \leftarrow f_{\textsc{Var}}^{(t)} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$
+		\State $\vec{X}_j^{(t)} \leftarrow f_\textsc{Assn}^{(t)} \hspace{-2pt} \big(\vec{V}_i^{(t-1)} \big)$ for all $j$ in $[n]$ 
 		\Statex
-		\Statex
-		\State $\vec{C}_j^{\hspace{1pt}(t)} \leftarrow {f}^{(t)}_{\text{C}} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_j, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_j \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$
+		%\State \textit{Compute constraint embedding:}
+		\State $\vec{C}_j^{\hspace{1pt}(t)} \leftarrow f_\textsc{Con}^{(t)} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_j, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_j \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$
 		%\State $\vec{e}_j^{(t)} \leftarrow \sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i - \vec{b}_j$
 		%\Statex
-		\State $\vec{p}_{j}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_{\text{P}}(\vec{e}^{(t)}))_{j}$
+		\State $\vec{p}_{j}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_\textsc{Prob}^{(t)}(\vec{e}^{(t)}))_{j}$
+		%\begin{equation*}
+		%\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \label{key}\vec{A}_{ji}  %\vec{v}_i \Big) - \vec{b}_j   
+		%\end{equation*}
 		\EndFor
-		\State $\bar{\vec{x}} \leftarrow f(\mathbin\Vert_{t \in [T]} \vec{x}^{(t)})$
-		\State $L \leftarrow L + \ell(\vec{\bar{x}}, \vec{\bar b})$ 
-		\State Gradient descent on $L$ with regard to $\boldsymbol{\theta}$
+		\State $\bar{\vec{X}}_j \leftarrow f_\textsc{Mrg}(\mathbin\Vert_{t \in [T]} \vec{X}_j^{(t)})$
+		\State $L \leftarrow L + \ell(\vec{\bar{X}}, \vec{\bar b})$ 
+		\State Gradient descent  with regard to $\boldsymbol{\theta}$
 		\EndFor
@@
 
+\begin{equation}\label{err}
+\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
+\end{equation}
+
 Initialize parameters $\boldsymbol{\theta} = (\boldsymbol{\theta}_{\text{V}}$, $\boldsymbol{\theta}_{\text{C}}$, $\boldsymbol{\theta}_{\text{X}}, \boldsymbol{\theta}_{\text{P}})$
 
-\subsection{Connnection to boosting}
+\subsection{Sample complexity}
 
-joint MWU and boosting
+\cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
+Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree
+
+\cm{Connection to Stefanies and Keyulus reasoning paper}
 

### 2020-08-19 gnn_models/mip_bipartite_class.py

@@ -93,8 +93,6 @@ class SimpleNet(torch.nn.Module):
 
         x = self.var_con_1(var_node_features, edge_index_var, edge_features_var, (num_nodes_var.sum(), num_nodes_con.sum()))
 
-
-
         x = F.relu(self.lin1(x))
         x = F.dropout(x, p=0.5, training=self.training)
         x = self.lin2(x)

### 2020-08-19 paper/main.tex
Cont. implementing new model.

@@
 	\item GNNs to solve MIPs/comb.
-optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gasse+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},
+optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gas+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},
 
@@
 \cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
-Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree
+Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds
 

### 2020-08-19 paper/main.tex
Cont. implementing new model.

@@
 
-\subsection{Sample complexity}
+\subsection{Sample complexity/theoretical justification}
 
 \cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
-Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds
+Proof idea: show that GNN can be seen as low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds
+
+\cm{Somehow show that architecture of Alg. 2 (MWU) is better than using a standard GNN. Idea: Show that MWU can be recovered to show to always get at ferasible solutions.}
 

### 2020-08-19 gnn_models/mip_bipartite_class.py

@@ -20,32 +20,25 @@ from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
 from torch_geometric.nn.inits import reset
 
-
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
 class SimpleBipartiteLayer(MessagePassing):
-    def __init__(self, edge_dim, dim_init, dim):
+    def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.edge_encoder = Sequential(Linear(edge_dim, dim_init), ReLU(), Linear(dim_init, dim_init), ReLU(),
-                                       BN(dim_init))
-        self.mlp = Sequential(Linear(dim_init, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
+        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+
+        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
         self.eps = torch.nn.Parameter(torch.Tensor([0]))
         self.initial_eps = 0
 
-    def forward(self, x, edge_index, edge_attr, size):
+    def forward(self, source, target, edge_index, edge_attr, size):
         edge_embedding = self.edge_encoder(edge_attr)
+        tmp = self.propagate(edge_index, x=source, edge_attr=edge_embedding, size=size)
 
-        print(x.size(), edge_index.size(), edge_attr.size())
-        print(size)
-
-        tmp = self.propagate(edge_index, x=x, edge_attr=edge_embedding, size=size)
-        print(tmp)
-        exit()
-
-        out = self.mlp((1 + self.eps) * x + tmp)
-
+        out = self.mlp((1 + self.eps) * target + tmp)
 
         return out
 
@@ -56,6 +49,7 @@ class SimpleBipartiteLayer(MessagePassing):
         return aggr_out
 
     def reset_parameters(self):
+        reset(self.node_encoder)
         reset(self.edge_encoder)
         reset(self.mlp)
         self.eps.data.fill_(self.initial_eps)
@@ -64,9 +58,13 @@ class SimpleBipartiteLayer(MessagePassing):
 class SimpleNet(torch.nn.Module):
     def __init__(self, hidden):
[…]

### 2020-08-19 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -353,8 +353,8 @@ for epoch in range(1, 100):
         break
 
     print(lr)
-    print('Epoch: {:03d}, Train Loss: {:.7f}, '
-          'Train Acc: {:.7f}, Test Acc: {:.7f}'.format(epoch, train_loss,
+    print('Epoch: {:03d}, LR: {:.7f}, Train Loss: {:.7f},  '
+          'Train Acc: {:.7f}, Test Acc: {:.7f}'.format(epoch, lr, train_loss,
                                                        train_acc, test_acc))
 
 torch.save(model.state_dict(), "trained_model_er_200_SET2_1k")

### 2020-08-19 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -65,6 +65,9 @@ class SimpleNet(torch.nn.Module):
         self.var_con_1 = SimpleBipartiteLayer(1, hidden)
         self.con_var_1 = SimpleBipartiteLayer(1, hidden)
         self.var_con_2 = SimpleBipartiteLayer(1, hidden)
+        self.con_var_2 = SimpleBipartiteLayer(1, hidden)
+        self.var_con_3 = SimpleBipartiteLayer(1, hidden)
+        self.con_var_3 = SimpleBipartiteLayer(1, hidden)
 
         self.lin1 = Linear(hidden, hidden)
         self.lin2 = Linear(hidden, 2)
@@ -96,14 +99,21 @@ class SimpleNet(torch.nn.Module):
 
         con_node_features_1 = self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
                            (num_nodes_var.sum(), num_nodes_con.sum()))
-
         var_node_features_1 = self.con_var_1(con_node_features_1, var_node_features_0, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum()))
 
+        con_node_features_2 = self.var_con_2(var_node_features_1, con_node_features_1, edge_index_var, edge_features_var,
+                           (num_nodes_var.sum(), num_nodes_con.sum()))
+        var_node_features_2 = self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
+                           (num_nodes_con.sum(), num_nodes_var.sum()))
+
+        con_node_features_3 = self.var_con_4(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
+                           (num_nodes_var.sum(), num_nodes_con.sum()))
+        var_node_features_3 = self.con_var_4(con_node_features_3, var_node_features_1, edge_index_con, edge_features_con,
+                           (num_nodes_con.sum(), num_nodes_var.sum()))
 
 
-
-        x = F.relu(self.lin1(var_node_features_1))
+        x = F.relu(self.lin1(var_node_features_3))
         x = F.dropout(x, p=0.5, training=self.training)
         x = self.lin2(x)
         return F.log_softmax(x, dim=-1)

### 2020-08-19 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -107,9 +107,9 @@ class SimpleNet(torch.nn.Module):
         var_node_features_2 = self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum()))
 
-        con_node_features_3 = self.var_con_4(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
+        con_node_features_3 = self.var_con_3(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
                            (num_nodes_var.sum(), num_nodes_con.sum()))
-        var_node_features_3 = self.con_var_4(con_node_features_3, var_node_features_1, edge_index_con, edge_features_con,
+        var_node_features_3 = self.con_var_3(con_node_features_3, var_node_features_1, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum()))
 
 

### 2020-08-19 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -87,7 +87,6 @@ class SimpleNet(torch.nn.Module):
         edge_index_var = data.edge_index_var
         edge_index_con = data.edge_index_con
 
-
         edge_features_var = data.edge_features_var
         edge_features_con = data.edge_features_con
         num_nodes_var = data.num_nodes_var
@@ -364,7 +363,7 @@ for epoch in range(1, 100):
 
     print(lr)
     print('Epoch: {:03d}, LR: {:.7f}, Train Loss: {:.7f},  '
-          'Train Acc: {:.7f}, Test Acc: {:.7f}'.format(epoch, lr, train_loss,
-                                                       train_acc, test_acc))
+          'Train Acc: {:.7f}, Val Acc: {:.7f}, Test Acc: {:.7f}'.format(epoch, lr, train_loss,
+                                                       train_acc, val_acc, test_acc))
 
 torch.save(model.state_dict(), "trained_model_er_200_SET2_1k")

### 2020-08-20 paper/main.tex
Cont. implementing new model.

@@
 optimization problems, \cite{Li+2018b}, \cite{Vel+2020}, \cite{Gas+2019} \cite{Gup+2020} \cite{Kha+2016}, paper by Bistra Dilkina: \cite{Fer+2020} \cite{Son+2020} \cite{Wil+2019} \cite{Kha+2016b}, Paper by Lodi \cite{Ben+2018}, \cite{Lar+2018}, \cite{Bon+2018}, \cite{Ben+2019}, \cite{Fis+2019}, \cite{Gup+2020}, \cite{Zar+2020},
+	Paper of bello, kool	1q§
 
@@
 \cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
-Proof idea: show that GNN can be seen as low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds
+\cm{Proof idea: show that GNN can be seen as low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds, Problem: (1) we are ingnoring the invariances here (should be okay as incoperating invariances are only improving sample complexity) (2) f}
 

### 2020-08-20 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -68,9 +68,13 @@ class SimpleNet(torch.nn.Module):
         self.con_var_2 = SimpleBipartiteLayer(1, hidden)
         self.var_con_3 = SimpleBipartiteLayer(1, hidden)
         self.con_var_3 = SimpleBipartiteLayer(1, hidden)
+        self.var_con_4 = SimpleBipartiteLayer(1, hidden)
+        self.con_var_4 = SimpleBipartiteLayer(1, hidden)
 
         self.lin1 = Linear(hidden, hidden)
-        self.lin2 = Linear(hidden, 2)
+        self.lin2 = Linear(hidden, hidden)
+        self.lin3 = Linear(hidden, hidden)
+        self.lin4 = Linear(hidden, 2)
 
     def reset_parameters(self):
         self.var_con_1.reset_parameters()
@@ -79,6 +83,8 @@ class SimpleNet(torch.nn.Module):
 
         self.lin1.reset_parameters()
         self.lin2.reset_parameters()
+        self.lin3.reset_parameters()
+        self.lin4.reset_parameters()
 
     def forward(self, data):
         var_node_features = data.var_node_features
@@ -108,13 +114,19 @@ class SimpleNet(torch.nn.Module):
 
         con_node_features_3 = self.var_con_3(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
                            (num_nodes_var.sum(), num_nodes_con.sum()))
-        var_node_features_3 = self.con_var_3(con_node_features_3, var_node_features_1, edge_index_con, edge_features_con,
+        var_node_features_3 = self.con_var_3(con_node_features_3, var_node_features_2, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum()))
 
+        con_node_features_4 = self.var_con_4(var_node_features_3, con_node_features_3, edge_index_var, edge_features_var,
+                           (num_nodes_var.sum(), num_nodes_con.sum()))
+        var_node_features_4 = self.con_var_4(con_node_features_4, var_node_features_3, edge_index_con, edge_features_con,
+                           (num_nodes_con.sum(), num_nodes_var.sum()))
 
-        x = F.relu(self.lin1(var_node_features_3))
-        x = F.dropout(x, p=0.5, training=self.training)
+        x = F.relu(self.lin1(var_node_features_4))
+        #x = F.dropout(x, p=0.5, training=self.training)
         x = self.lin2(x)
[…]

### 2020-08-20 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -102,30 +102,30 @@ class SimpleNet(torch.nn.Module):
         con_node_features_0 = self.con_node_encoder(con_node_features)
 
 
-        con_node_features_1 = self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
-                           (num_nodes_var.sum(), num_nodes_con.sum()))
-        var_node_features_1 = self.con_var_1(con_node_features_1, var_node_features_0, edge_index_con, edge_features_con,
-                           (num_nodes_con.sum(), num_nodes_var.sum()))
+        con_node_features_1 = F.relu(self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
+                           (num_nodes_var.sum(), num_nodes_con.sum())))
+        var_node_features_1 = F.relu(self.con_var_1(con_node_features_1, var_node_features_0, edge_index_con, edge_features_con,
+                           (num_nodes_con.sum(), num_nodes_var.sum())))
 
-        con_node_features_2 = self.var_con_2(var_node_features_1, con_node_features_1, edge_index_var, edge_features_var,
-                           (num_nodes_var.sum(), num_nodes_con.sum()))
-        var_node_features_2 = self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
-                           (num_nodes_con.sum(), num_nodes_var.sum()))
+        con_node_features_2 = F.relu(self.var_con_2(var_node_features_1, con_node_features_1, edge_index_var, edge_features_var,
+                           (num_nodes_var.sum(), num_nodes_con.sum())))
+        var_node_features_2 = F.relu(self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
+                           (num_nodes_con.sum(), num_nodes_var.sum())))
 
-        con_node_features_3 = self.var_con_3(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
-                           (num_nodes_var.sum(), num_nodes_con.sum()))
-        var_node_features_3 = self.con_var_3(con_node_features_3, var_node_features_2, edge_index_con, edge_features_con,
-                           (num_nodes_con.sum(), num_nodes_var.sum()))
+        con_node_features_3 = F.relu(self.var_con_3(var_node_features_2, con_node_features_2, edge_index_var, edge_features_var,
[…]

### 2020-08-20 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -35,7 +35,9 @@ class SimpleBipartiteLayer(MessagePassing):
         self.initial_eps = 0
 
     def forward(self, source, target, edge_index, edge_attr, size):
+        # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
+
         tmp = self.propagate(edge_index, x=source, edge_attr=edge_embedding, size=size)
 
         out = self.mlp((1 + self.eps) * target + tmp)
@@ -59,9 +61,11 @@ class SimpleNet(torch.nn.Module):
     def __init__(self, hidden):
         super(SimpleNet, self).__init__()
 
+        # Embed initial node features.
         self.var_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
         self.con_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
 
+        # Bipartite GNN architecture.
         self.var_con_1 = SimpleBipartiteLayer(1, hidden)
         self.con_var_1 = SimpleBipartiteLayer(1, hidden)
         self.var_con_2 = SimpleBipartiteLayer(1, hidden)
@@ -71,6 +75,7 @@ class SimpleNet(torch.nn.Module):
         self.var_con_4 = SimpleBipartiteLayer(1, hidden)
         self.con_var_4 = SimpleBipartiteLayer(1, hidden)
 
+        # MLP used for classification.
         self.lin1 = Linear(hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
@@ -80,6 +85,11 @@ class SimpleNet(torch.nn.Module):
         self.var_con_1.reset_parameters()
         self.con_var_1.reset_parameters()
         self.var_con_2.reset_parameters()
+        self.con_var_2.reset_parameters()
+        self.var_con_3.reset_parameters()
+        self.con_var_3.reset_parameters()
+        self.var_con_4.reset_parameters()
+        self.con_var_4.reset_parameters()
 
         self.lin1.reset_parameters()
         self.lin2.reset_parameters()
@@ -87,17 +97,18 @@ class SimpleNet(torch.nn.Module):
         self.lin4.reset_parameters()
 
     def forward(self, data):
+
+        # Get data of batch.
         var_node_features = data.var_node_features
         con_node_features = data.con_node_features
-
         edge_index_var = data.edge_index_var
[…]

### 2020-08-20 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -76,7 +76,7 @@ class SimpleNet(torch.nn.Module):
         self.con_var_4 = SimpleBipartiteLayer(1, hidden)
 
         # MLP used for classification.
-        self.lin1 = Linear(hidden, hidden)
+        self.lin1 = Linear(5*hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
@@ -132,6 +132,8 @@ class SimpleNet(torch.nn.Module):
                            (num_nodes_var.sum(), num_nodes_con.sum())))
         var_node_features_4 = F.relu(self.con_var_4(con_node_features_4, var_node_features_3, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum())))
+
+        x = torch.cat([var_node_features_0,var_node_features_1,var_node_features_2,var_node_features_3,var_node_features_4], dim=-1)
 
         x = F.relu(self.lin1(var_node_features_4))
         x = F.dropout(x, p=0.5, training=self.training)
@@ -243,7 +245,7 @@ class GraphDataset(InMemoryDataset):
                 # Source node is con, target node is var.
 
                 if graph.nodes[s]['bipartite'] == 1:
-                    # Source node ist constraint. C->V.
+                    # Source node is constraint. C->V.
                     edge_list_con.append([node_to_connode[s], node_to_varnode[t]])
                     edge_features_con.append([edge_data['coeff']])
                 else:
@@ -319,7 +321,7 @@ print(len(test_dataset))
 print(1 - test_dataset.data.y.sum().item() / test_dataset.data.y.size(-1))
 
 # Prepare batch loaders.
-batch_size = 25
+batch_size = 128
 train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
 val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=True)
 test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)

### 2020-08-20 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -135,7 +135,7 @@ class SimpleNet(torch.nn.Module):
 
         x = torch.cat([var_node_features_0,var_node_features_1,var_node_features_2,var_node_features_3,var_node_features_4], dim=-1)
 
-        x = F.relu(self.lin1(var_node_features_4))
+        x = F.relu(self.lin1(x))
         x = F.dropout(x, p=0.5, training=self.training)
         x = F.relu(self.lin2(x))
         x = F.dropout(x, p=0.5, training=self.training)

### 2020-08-21 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -329,7 +329,7 @@ test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
 
 print("### DATA LOADED.")
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-model = SimpleNet(hidden=64).to(device)
+model = SimpleNet(hidden=256).to(device)
 optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
 
 # Play with this.

### 2020-08-21 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -329,7 +329,7 @@ test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
 
 print("### DATA LOADED.")
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-model = SimpleNet(hidden=256).to(device)
+model = SimpleNet(hidden=128).to(device)
 optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
 
 # Play with this.

### 2020-08-21 gnn_models/mip_bipartite_class.py
Cont. implementing new model.

@@ -25,7 +25,8 @@ device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
-        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+        # TODO add
+        super(SimpleBipartiteLayer, self).__init__(aggr="mean", flow="source_to_target")
 
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))

### 2020-09-16 model_execution/inference.py
adding some MIP testing code

@@ -1,0 +1,233 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+import argparse
+
+import torch
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+from gnn_models.baselines.mpnn_architecture_class import Net
+
+import cplex
+
+import callbacks_cplex
+
+def get_prediction(model_name, graph):
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+    model = Net(dim=64).to(device)
+    model.load_state_dict(torch.load(model_name, map_location=device))
+
+
+    data, var_node, node_var = create_data_object(graph)
+    model.eval()
+
+    data = data.to(device)
+
+    # out = model(data).max(dim=1)[1].cpu().detach().numpy()
+    out = model(data).exp()[:,1].cpu().detach().numpy()
+
+    return out, node_var, var_node
+
+def create_data_object(graph):
+    # Make graph directed.
+    graph = nx.convert_node_labels_to_integers(graph)
+    graph = graph.to_directed() if not nx.is_directed(graph) else graph
+    data = Data()
+    edge_index = torch.tensor(list(graph.edges)).t().contiguous()
+    data = Data(edge_index=edge_index)
+
+    #  Map for new nodes in graph.
+
+    # Original node to var nodes
+    var_node = {}
+    # Var node to orignal
+    node_var = {}
+
+    con_node = {}
+
+    assoc_var = []
+    assoc_con = []
+    node_type = []
+    # Number of variables.
+    var_i = 0
+    # Number of constraints.
+    con_i = 0
+    # Targets
+    y = []
+    # Features for variable nodes.
+    var_feat = []
+    # Feature for constraints nodes.
+    con_feat = []
+    # Right-hand sides of equations.
+    rhss = []
+    # Sums over coefficients.
+    a_sum = []
+    for i, (node, node_data) in enumerate(graph.nodes(data=True)):
+        # Node is a variable.
+        if node_data['bipartite'] == 0:
+            var_node[i] = var_i
+            node_type.append(0)
+            assoc_var.append(i)
+            node_var[var_i] = i
+            var_i += 1
+
+            if (node_data['bias'] < 0.05):
+                y.append(0)
+            else:
+                y.append(1)
[…]

### 2021-03-09 gnn_models/GIN/mip_bipartite_class.py
e

@@ -471,10 +471,10 @@ file_list = [
     #"../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/",
     # "../DATA1/er_SET2/200_200/alpha_0.25_setParam_100/train/",
     # "../DATA1/er_SET2/200_200/alpha_0.5_setParam_100/train/",
-    # "../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/",
+    "../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/",
     #"../DATA1/er_SET2/300_300/alpha_0.25_setParam_100/train/",
     # "../DATA1/er_SET2/300_300/alpha_0.5_setParam_100/train/",
-    "../DATA1/er_SET1/400_400/alpha_0.75_setParam_100/train/",
+    # "../DATA1/er_SET1/400_400/alpha_0.75_setParam_100/train/",
     # "../DATA1/er_SET1/400_400/alpha_0.5_setParam_100/train/",
     #"../DATA1/er_SET1/400_400/alpha_0.25_setParam_100/train/",
 ]
@@ -483,10 +483,10 @@ name_list = [
     # "er_SET2_200_200_alpha_0_75_setParam_100_train",
     # "er_SET2_200_200_alpha_0_25_setParam_100_train",
     # "er_SET2_200_200_alpha_0_5_setParam_100_train",
-    # "er_SET2_300_300_alpha_0_75_setParam_100_train",
+    "er_SET2_300_300_alpha_0_75_setParam_100_train",
     # "er_SET2_300_300_alpha_0_25_setParam_100_train",
     # "er_SET2_300_300_alpha_0_5_setParam_100_train",
-    "er_SET1_400_400_alpha_0_75_setParam_100_train",
+    # "er_SET1_400_400_alpha_0_75_setParam_100_train",
     # "er_SET1_400_400_alpha_0_5_setParam_100_train",
     #"er_SET1_400_400_alpha_0_25_setParam_100_train",
 ]

### 2021-03-09 gnn_models/GIN/mip_bipartite_simple_class.py

@@ -297,7 +297,7 @@ class MyTransform(object):
 # Prepare data.
 path = osp.join(osp.dirname(osp.realpath(__file__)), '.', 'data', 'DS')
 # Path to raw graph data.
-data_path = '../DATA1/er_SET1/400_400/alpha_0.75_setParam_100/train/'
+data_path = '../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/'
 # Threshold for computing class labels.
 bias_threshold = 0.05
 # Create dataset.

### 2021-03-09 gnn_models/GIN/mip_bipartite_class.py
e

@@ -471,7 +471,7 @@ file_list = [
     #"../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/",
     # "../DATA1/er_SET2/200_200/alpha_0.25_setParam_100/train/",
     # "../DATA1/er_SET2/200_200/alpha_0.5_setParam_100/train/",
-    "../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/",
+    "../../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/",
     #"../DATA1/er_SET2/300_300/alpha_0.25_setParam_100/train/",
     # "../DATA1/er_SET2/300_300/alpha_0.5_setParam_100/train/",
     # "../DATA1/er_SET1/400_400/alpha_0.75_setParam_100/train/",

### 2021-03-09 gnn_models/GIN/mip_bipartite_simple_class.py

@@ -297,7 +297,7 @@ class MyTransform(object):
 # Prepare data.
 path = osp.join(osp.dirname(osp.realpath(__file__)), '.', 'data', 'DS')
 # Path to raw graph data.
-data_path = '../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/'
+data_path = '../../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/'
 # Threshold for computing class labels.
 bias_threshold = 0.05
 # Create dataset.

### 2021-03-09 gnn_models/NNconv/inference.py
e

@@ -1,0 +1,140 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+
+import torch
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+from gnn_models.mip_bipartite_arch import SimpleNet
+
+
+
+def get_prediction(model_name, graph, bias_threshold=0.05):
+    device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+    model = SimpleNet(128).to(device)
+    model.load_state_dict(torch.load(model_name, map_location=device))
+
+
+    data, var_node, node_var = create_data_object(graph, bias_threshold)
+    model.eval()
+
+    data = data.to(device)
+
+    out = model(data).max(dim=1)[1].cpu().detach().numpy()
+
+    return out
+
+def create_data_object(graph, bias_threshold):
+    # Make graph directed.
+    graph = nx.convert_node_labels_to_integers(graph)
+    graph = graph.to_directed() if not nx.is_directed(graph) else graph
+    data = Data()
+
+    #  Maps networkx ids to new variable node ids.
+    node_to_varnode = {}
+    #  Maps networkx ids to new constraint node ids.
+    node_to_connode = {}
+
+    # Number of variables.
+    num_nodes_var = 0
+    # Number of constraints.
+    num_nodes_con = 0
+    # Targets (classes).
+    y = []
+    # Features for variable nodes.
+    feat_var = []
+    # Feature for constraints nodes.
+    feat_con = []
+    # Right-hand sides of equations.
+    feat_rhs = []
+
+    index = []
+    index_var = []
+    obj = []
+
+    # Iterate over nodes, and collect features.
+    for i, (node, node_data) in enumerate(graph.nodes(data=True)):
+        # Node is a variable node.
+        if node_data['bipartite'] == 0:
+            node_to_varnode[i] = num_nodes_var
+            num_nodes_var += 1
+
+            if (node_data['bias'] < bias_threshold):
+                y.append(0)
+            else:
+                y.append(1)
+
+            feat_var.append([node_data['objcoeff'], graph.degree[i]])
+            obj.append([node_data['objcoeff']])
+            index_var.append(0)
+
+        # Node is constraint node.
+        elif node_data['bipartite'] == 1:
[…]

### 2021-03-09 gnn_models/NNconv/mip_bipartite_class.py

@@ -1,0 +1,609 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+from sklearn.model_selection import train_test_split
+
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+
+import torch_geometric.utils.softmax
+
+import torch
+
+import torch.nn.functional as F
+from torch.nn import BatchNorm1d as BN
+from torch.nn import Sequential, Linear, ReLU, Sigmoid
+from torch_geometric.nn import MessagePassing
+from torch_geometric.nn.inits import reset
+
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+# Update constraint embeddings based on variable embeddings.
+class VarConBipartiteLayer(MessagePassing):
+    def __init__(self, edge_dim, dim, var_assigment):
+        super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        # Maps edge features to the same number of components as node features.
+        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+
+        # Maps variable embeddings to scalar variable assigment.
+        self.var_assigment = var_assigment
+        # Maps variable embeddings + assignment to joint embedding.
+        self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                    BN(dim))
+
+        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                              BN(dim))
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
+
+    def forward(self, source, target, edge_index, edge_attr, rhs, size):
+        # Map edge features to embeddings with the same number of components as node embeddings.
+        edge_embedding = self.edge_encoder(edge_attr)
+        # Compute scalar variable assignment.
+        var_assignment = self.var_assigment(source)
+        # Compute joint embedding of variable embeddings and scalar variable assignment.
+        new_source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
+
+        # Do the acutal message passing.
[…]

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py

@@ -1,0 +1,417 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+from sklearn.model_selection import train_test_split
+
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+
+import torch
+import torch.nn.functional as F
+from torch.nn import BatchNorm1d as BN
+from torch.nn import Sequential, Linear, ReLU
+from torch_geometric.nn import MessagePassing
+
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+
+from typing import Union, Tuple, Callable
+from torch_geometric.typing import OptTensor, OptPairTensor, Adj, Size
+
+import torch
+from torch import Tensor
+from torch.nn import Parameter
+from torch_geometric.nn.conv import MessagePassing
+
+from torch_geometric.nn.inits import reset, uniform, zeros
+
+
+class SimpleBipartiteLayer(MessagePassing):
+
+    def __init__(self, edge_dim, dim):
+        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        self.nn = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+
+        self.dim = dim
+
+        self.root = Parameter(torch.Tensor(dim, dim))
+        self.bias = Parameter(torch.Tensor(dim))
+
+        self.reset_parameters()
+
+    def reset_parameters(self):
+        reset(self.nn)
+        if self.root is not None:
+            uniform(self.root.size(0), self.root)
+        zeros(self.bias)
+
+    def forward(self, source, target, edge_index, edge_attr, size) -> Tensor:
+
+        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
+
+        out += torch.matmul(target, self.root)
+        out += self.bias
+
+        return out
+
+    def message(self, x_j, edge_attr):
+        weight = self.nn(edge_attr)
+        weight = weight.view(-1, self.dim, self.dim)
+        return torch.matmul(x_j.unsqueeze(1), weight).squeeze(1)
+
+    def __repr__(self):
+        return '{}({}, {})'.format(self.__class__.__name__, self.in_channels,
+                                   self.out_channels)
+
[…]

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -66,6 +66,10 @@ class SimpleBipartiteLayer(MessagePassing):
     def message(self, x_j, edge_attr):
         weight = self.nn(edge_attr)
         weight = weight.view(-1, self.dim, self.dim)
+
+        print(weight.size(), x_j.unsqueeze(1).size())
+        exit()
+
         return torch.matmul(x_j.unsqueeze(1), weight).squeeze(1)
 
     def __repr__(self):

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -65,6 +65,9 @@ class SimpleBipartiteLayer(MessagePassing):
 
     def message(self, x_j, edge_attr):
         weight = self.nn(edge_attr)
+
+        print(weight.size())
+        exit()
         weight = weight.view(-1, self.dim, self.dim)
 
         print(weight.size(), x_j.unsqueeze(1).size())

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -38,8 +38,8 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
+        self.nn = Sequential(Linear(edge_dim, dim*dim), ReLU(), Linear(dim*dim, dim*dim), ReLU(),
+                                       BN(dim*dim))
 
         self.dim = dim
 

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -66,9 +66,9 @@ class SimpleBipartiteLayer(MessagePassing):
     def message(self, x_j, edge_attr):
         weight = self.nn(edge_attr)
 
+        weight = weight.view(-1, self.dim, self.dim)
         print(weight.size())
         exit()
-        weight = weight.view(-1, self.dim, self.dim)
 
         print(weight.size(), x_j.unsqueeze(1).size())
         exit()

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -358,7 +358,7 @@ test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)
 
 print("### DATA LOADED.")
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-model = SimpleNet(hidden=128).to(device)
+model = SimpleNet(hidden=32).to(device)
 optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
 
 # Play with this.

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -67,8 +67,6 @@ class SimpleBipartiteLayer(MessagePassing):
         weight = self.nn(edge_attr)
 
         weight = weight.view(-1, self.dim, self.dim)
-        print(weight.size())
-        exit()
 
         print(weight.size(), x_j.unsqueeze(1).size())
         exit()

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -68,9 +68,6 @@ class SimpleBipartiteLayer(MessagePassing):
 
         weight = weight.view(-1, self.dim, self.dim)
 
-        print(weight.size(), x_j.unsqueeze(1).size())
-        exit()
-
         return torch.matmul(x_j.unsqueeze(1), weight).squeeze(1)
 
     def __repr__(self):

### 2021-03-09 gnn_models/NNconv/mip_bipartite_simple_class.py
e

@@ -345,7 +345,7 @@ print(len(test_dataset))
 print(1 - test_dataset.data.y.sum().item() / test_dataset.data.y.size(-1))
 
 # Prepare batch loaders.
-batch_size = 15
+batch_size = 2
 train_loader = DataLoader(train_dataset, batch_size=batch_size, shuffle=True)
 val_loader = DataLoader(val_dataset, batch_size=batch_size, shuffle=True)
 test_loader = DataLoader(test_dataset, batch_size=batch_size, shuffle=True)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -1,0 +1,392 @@
+import sys
+
+sys.path.insert(0, '..')
+sys.path.insert(0, '../..')
+sys.path.insert(0, '.')
+
+import os
+import os.path as osp
+import numpy as np
+import networkx as nx
+from sklearn.model_selection import train_test_split
+
+from torch_geometric.data import (InMemoryDataset, Data)
+from torch_geometric.data import DataLoader
+
+import torch
+import torch.nn.functional as F
+from torch.nn import BatchNorm1d as BN
+from torch.nn import Sequential, Linear, ReLU
+from torch_geometric.nn import MessagePassing
+from torch_geometric.nn.inits import reset
+
+device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+
+
+class SimpleBipartiteLayer(MessagePassing):
+
+    def __init__(self, edge_dim, dim, aggr = "max"):
+        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        self.nn = Sequential(Linear(2*dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+        self.reset_parameters()
+
+    def reset_parameters(self):
+        reset(self.nn)
+
+    def forward(self,  source, target, edge_index, edge_attr, size):
+
+        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
+
+        return out
+
+    def message(self, x_i, x_j, edge_attr):
+        return self.nn(torch.cat([x_i, x_j - x_i, edge_attr], dim=-1))
+
+    def __repr__(self):
+        return '{}(nn={})'.format(self.__class__.__name__, self.nn)
+
+
+
+class SimpleNet(torch.nn.Module):
+    def __init__(self, hidden):
+        super(SimpleNet, self).__init__()
+
+        # Embed initial node features.
+        self.var_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
+        self.con_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
+
+        # Bipartite GNN architecture.
+        self.var_con_1 = SimpleBipartiteLayer(1, hidden)
+        self.con_var_1 = SimpleBipartiteLayer(1, hidden)
+        self.var_con_2 = SimpleBipartiteLayer(1, hidden)
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_simple_class.py

@@ -18,62 +18,41 @@ import torch.nn.functional as F
 from torch.nn import BatchNorm1d as BN
 from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
+from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
-from typing import Union, Tuple, Callable
-from torch_geometric.typing import OptTensor, OptPairTensor, Adj, Size
-
-import torch
-from torch import Tensor
-from torch.nn import Parameter
-from torch_geometric.nn.conv import MessagePassing
-
-from torch_geometric.nn.inits import reset, uniform, zeros
-
-
-class SimpleBipartiteLayer(MessagePassing):
-
+class SimpleLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
-        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+        super(SimpleLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(edge_dim, dim*dim), ReLU(), Linear(dim*dim, dim*dim), ReLU(),
-                                       BN(dim*dim))
+        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
 
-        self.dim = dim
+        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
 
-        self.root = Parameter(torch.Tensor(dim, dim))
-        self.bias = Parameter(torch.Tensor(dim))
+    def forward(self, x, edge_index, edge_attr):
+        # Map edge features to embeddings with the same number of components as node embeddings.
+        edge_embedding = self.edge_encoder(edge_attr)
+        tmp = self.propagate(edge_index, x=x, edge_attr=edge_embedding)
 
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
-        if self.root is not None:
-            uniform(self.root.size(0), self.root)
-        zeros(self.bias)
-
-    def forward(self, source, target, edge_index, edge_attr, size) -> Tensor:
-
-        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
-
-        out += torch.matmul(target, self.root)
-        out += self.bias
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -35,14 +35,14 @@ class SimpleBipartiteLayer(MessagePassing):
     def reset_parameters(self):
         reset(self.nn)
 
-    def forward(self,  source, target, edge_index, edge_attr, size):
+    def forward(self, source, target, edge_index, edge_attr, size):
 
-        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
+        out = self.propagate(edge_index, x=source, t = target, edge_attr=edge_attr, size=size)
 
         return out
 
-    def message(self, x_i, x_j, edge_attr):
-        return self.nn(torch.cat([x_i, x_j - x_i, edge_attr], dim=-1))
+    def message(self, x_i, t_j, edge_attr):
+        return self.nn(torch.cat([x_i, t_j - x_i, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -28,7 +28,7 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim, aggr = "max"):
         super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(2*dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
         self.reset_parameters()
 
@@ -37,12 +37,12 @@ class SimpleBipartiteLayer(MessagePassing):
 
     def forward(self, source, target, edge_index, edge_attr, size):
 
-        out = self.propagate(edge_index, x=source, t = target, edge_attr=edge_attr, size=size)
+        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
 
         return out
 
-    def message(self, x_i, t_j, edge_attr):
-        return self.nn(torch.cat([x_i, t_j - x_i, edge_attr], dim=-1))
+    def message(self, x_j, edge_attr):
+        return self.nn(torch.cat([x_j, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -25,8 +25,8 @@ device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 class SimpleBipartiteLayer(MessagePassing):
 
-    def __init__(self, edge_dim, dim, aggr = "max"):
-        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+    def __init__(self, edge_dim, dim):
+        super(SimpleBipartiteLayer, self).__init__(aggr="max", flow="source_to_target")
 
         self.nn = Sequential(Linear(dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -37,11 +37,11 @@ class SimpleBipartiteLayer(MessagePassing):
 
     def forward(self, source, target, edge_index, edge_attr, size):
 
-        out = self.propagate(edge_index, x=source, edge_attr=edge_attr, size=size)
+        out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_attr, size=size)
 
         return out
 
-    def message(self, x_j, edge_attr):
+    def message(self, x_j, t_i, edge_attr):
         return self.nn(torch.cat([x_j, edge_attr], dim=-1))
 
     def __repr__(self):

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py
e

@@ -28,7 +28,7 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="max", flow="source_to_target")
 
-        self.nn = Sequential(Linear(dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(2*dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
         self.reset_parameters()
 
@@ -42,7 +42,7 @@ class SimpleBipartiteLayer(MessagePassing):
         return out
 
     def message(self, x_j, t_i, edge_attr):
-        return self.nn(torch.cat([x_j, edge_attr], dim=-1))
+        return self.nn(torch.cat([t_i, x_j, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -25,13 +25,12 @@ from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
-# Update constraint embeddings based on variable embeddings.
 class VarConBipartiteLayer(MessagePassing):
+
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        # Maps edge features to the same number of components as node features.
-        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(2*dim + edge_dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
         # Maps variable embeddings to scalar variable assigment.
@@ -40,39 +39,25 @@ class VarConBipartiteLayer(MessagePassing):
         self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                     BN(dim))
 
-        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                              BN(dim))
-        self.eps = torch.nn.Parameter(torch.Tensor([0]))
-        self.initial_eps = 0
+        self.reset_parameters()
+
+    def reset_parameters(self):
+        reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
-        # Compute joint embedding of variable embeddings and scalar variable assignment.
-        new_source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
 
-        # Do the acutal message passing.
-        tmp = self.propagate(edge_index, x=new_source, var_assignment=var_assignment, edge_attr=edge_embedding,
-                             size=size)
-        out = self.mlp((1 + self.eps) * target + tmp)
+        out = self.propagate(edge_index, x=source, t=target, v=var_assignment, edge_attr=edge_attr, size=size)
 
         return out
 
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_simple_class.py

@@ -1,361 +1,0 @@
-import sys
-
-sys.path.insert(0, '..')
-sys.path.insert(0, '../..')
-sys.path.insert(0, '.')
-
-import os
-import os.path as osp
-import numpy as np
-import networkx as nx
-from sklearn.model_selection import train_test_split
-
-from torch_geometric.data import (InMemoryDataset, Data)
-from torch_geometric.data import DataLoader
-
-import torch
-import torch.nn.functional as F
-from torch.nn import BatchNorm1d as BN
-from torch.nn import Sequential, Linear, ReLU
-from torch_geometric.nn import MessagePassing
-from torch_geometric.nn.inits import reset
-
-device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-
-
-class SimpleLayer(MessagePassing):
-    def __init__(self, edge_dim, dim):
-        super(SimpleLayer, self).__init__(aggr="add", flow="source_to_target")
-
-        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
-
-        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
-        self.eps = torch.nn.Parameter(torch.Tensor([0]))
-        self.initial_eps = 0
-
-    def forward(self, x, edge_index, edge_attr):
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
-        tmp = self.propagate(edge_index, x=x, edge_attr=edge_embedding)
-
-        out = self.mlp((1 + self.eps) * x + tmp)
-
-        return out
-
-    def message(self, x_j, edge_attr):
-        return F.relu(x_j + edge_attr)
-
-    def update(self, aggr_out):
-        return aggr_out
-
-    def reset_parameters(self):
-        reset(self.edge_encoder)
-        reset(self.mlp)
-        self.eps.data.fill_(self.initial_eps)
-
-
-class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden):
-        super(SimpleNet, self).__init__()
-
-        # Embed initial node features.
-        self.var_node_encoder = Sequential(Linear(3, hidden), ReLU(), Linear(hidden, hidden))
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -30,14 +30,16 @@ class VarConBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(2*dim + edge_dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(2*dim + dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+
+
+        # Maps edge features to the same number of components as node features.
+        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
-        # Maps variable embeddings + assignment to joint embedding.
-        self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                    BN(dim))
 
         self.reset_parameters()
 
@@ -48,7 +50,10 @@ class VarConBipartiteLayer(MessagePassing):
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
 
-        out = self.propagate(edge_index, x=source, t=target, v=var_assignment, edge_attr=edge_attr, size=size)
+        # Map edge features to embeddings with the same number of components as node embeddings.
+        edge_embedding = self.edge_encoder(edge_attr)
+
+        out = self.propagate(edge_index, x=source, t=target, v=var_assignment, edge_attr=edge_embedding, size=size)
 
         return out
 

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -167,6 +167,10 @@ class ConVarBipartiteLayer(MessagePassing):
         return out
 
     def message(self, x_j, t_i, e_j, edge_attr):
+        print(torch.cat([t_i, x_j, e_j, edge_attr], dim=-1).size())
+
+        exit()
+
         return self.nn(torch.cat([t_i, x_j, e_j, edge_attr], dim=-1))
 
     def __repr__(self):

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -148,12 +148,12 @@ class ConVarBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(ConVarBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(2*dim + edge_dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(2*dim + edge_dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
         # Learn joint representation of contraint embedding and error.
-        self.joint_con_encoder = Sequential(Linear(dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                            BN(dim))
+        #self.joint_con_encoder = Sequential(Linear(dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+        #                                    BN(dim))
 
         self.reset_parameters()
 

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -167,9 +167,7 @@ class ConVarBipartiteLayer(MessagePassing):
         return out
 
     def message(self, x_j, t_i, e_j, edge_attr):
-        print(torch.cat([t_i, x_j, e_j, edge_attr], dim=-1).size())
-
-        exit()
+     
 
         return self.nn(torch.cat([t_i, x_j, e_j, edge_attr], dim=-1))
 

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -67,16 +67,22 @@ class VarConBipartiteLayer(MessagePassing):
 
 # Compute error signal.
 class ErrorLayer(MessagePassing):
-    def __init__(self, dim, var_assignment):
+    def __init__(self, edge_dim, dim, var_assignment):
         super(ErrorLayer, self).__init__(aggr="add", flow="source_to_target")
         self.var_assignment = var_assignment
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                         BN(dim))
 
+
+
     # TODO: Change back!
     def forward(self, source, edge_index, edge_attr, rhs, index, size):
         # Compute scalar variable assignment.
         new_source = self.var_assignment(source)
+
+        # Map edge features to embeddings with the same number of components as node embeddings.
+
+
         tmp = self.propagate(edge_index, x=new_source, edge_attr=edge_attr, size=size)
 
         # Compute residual, i.e., Ax-b.
@@ -99,56 +105,16 @@ class ErrorLayer(MessagePassing):
         return aggr_out
 
 
-# Update variable embeddings based on constraint embeddings.
 class ConVarBipartiteLayer(MessagePassing):
+
     def __init__(self, edge_dim, dim):
         super(ConVarBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        self.nn = Sequential(Linear(4*dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
-
-        # Learn joint representation of contraint embedding and error.
-        self.joint_con_encoder = Sequential(Linear(dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                            BN(dim))
-
-        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
-        self.eps = torch.nn.Parameter(torch.Tensor([0]))
-        self.initial_eps = 0
-
-    def forward(self, source, target, edge_index, edge_attr, error_con, size):
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -67,7 +67,7 @@ class VarConBipartiteLayer(MessagePassing):
 
 # Compute error signal.
 class ErrorLayer(MessagePassing):
-    def __init__(self, edge_dim, dim, var_assignment):
+    def __init__(self, dim, var_assignment):
         super(ErrorLayer, self).__init__(aggr="add", flow="source_to_target")
         self.var_assignment = var_assignment
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -25,14 +25,15 @@ from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
+
 class VarConBipartiteLayer(MessagePassing):
 
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(2*dim + dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
-
+        # Combine node and edge features of adjacent nodes.
+        self.nn = Sequential(Linear(3 * dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                             BN(dim))
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
@@ -57,12 +58,11 @@ class VarConBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j, t_i, v_j, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
+    def message(self, x_j, t_i, v_i, edge_attr):
+        return self.nn(torch.cat([t_i, x_j, v_i, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)
-
 
 
 # Compute error signal.
@@ -73,15 +73,10 @@ class ErrorLayer(MessagePassing):
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                         BN(dim))
 
-
-
     # TODO: Change back!
     def forward(self, source, edge_index, edge_attr, rhs, index, size):
         # Compute scalar variable assignment.
         new_source = self.var_assignment(source)
-
-        # Map edge features to embeddings with the same number of components as node embeddings.
-
 
         tmp = self.propagate(edge_index, x=new_source, edge_attr=edge_attr, size=size)
 
@@ -110,15 +105,15 @@ class ConVarBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -58,8 +58,8 @@ class VarConBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j, t_i, v_i, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_i, edge_attr], dim=-1))
+    def message(self, x_j, t_i, v_j, edge_attr):
+        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -49,7 +49,7 @@ class VarConBipartiteLayer(MessagePassing):
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
         # Compute scalar variable assignment.
-        var_assignment = self.var_assigment(source)
+        var_assignment = self.var_assigment(target)
 
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
@@ -58,8 +58,8 @@ class VarConBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j, t_i, v_j, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
+    def message(self, x_j, t_i, v_i, edge_attr):
+        return self.nn(torch.cat([t_i, x_j, v_i, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -73,7 +73,6 @@ class ErrorLayer(MessagePassing):
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                         BN(dim))
 
-    # TODO: Change back!
     def forward(self, source, edge_index, edge_attr, rhs, index, size):
         # Compute scalar variable assignment.
         new_source = self.var_assignment(source)
@@ -83,10 +82,8 @@ class ErrorLayer(MessagePassing):
         # Compute residual, i.e., Ax-b.
         out = tmp - rhs
 
-        # TODO: Think here.
         out = self.error_encoder(out)
 
-        # TODO: Change.
         out = torch_geometric.utils.softmax(out, index)
 
         return out
@@ -111,10 +108,6 @@ class ConVarBipartiteLayer(MessagePassing):
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
-
-        # Learn joint representation of contraint embedding and error.
-        # self.joint_con_encoder = Sequential(Linear(dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-        #                                    BN(dim))
 
         self.reset_parameters()
 
@@ -208,11 +201,8 @@ class SimpleNet(torch.nn.Module):
         edge_index_con = data.edge_index_con
         edge_features_var = data.edge_features_var
         edge_features_con = data.edge_features_con
-        num_nodes_var = data.num_nodes_var
-        num_nodes_con = data.num_nodes_con
         rhs = data.rhs
         index = data.index
-        obj = data.obj
 
         # Compute initial node embeddings.
         var_node_features_0 = self.var_node_encoder(var_node_features)
@@ -257,18 +247,6 @@ class SimpleNet(torch.nn.Module):
         var_node_features_4 = F.relu(
             self.con_var_4(con_node_features_4, var_node_features_3, edge_index_con, edge_features_con, err_4,
                            (con_node_features_4.size(0), var_node_features_3.size(0))))
-
-        var = self.var_assigment_4(var_node_features_4)
-
-        # cost = torch.mul(var, obj)
-        # print(cost.size())
-        # print(data.index_var)
-        # cost = scatter_add(cost, index=data.index_var, dim=0)
-        #
-        # print(cost.size())
-        # exit()
-
[…]

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_simple_class.py

@@ -28,16 +28,23 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="max", flow="source_to_target")
 
-        self.nn = Sequential(Linear(2*dim + edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+        self.nn = Sequential(Linear(3*dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
+
+        # Maps edge features to the same number of components as node features.
+        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                       BN(dim))
+
         self.reset_parameters()
 
     def reset_parameters(self):
         reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
+        # Map edge features to embeddings with the same number of components as node embeddings.
+        edge_embedding = self.edge_encoder(edge_attr)
 
-        out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_attr, size=size)
+        out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size)
 
         return out
 

### 2021-03-09 gnn_models/EdgeConv/mip_bipartite_class.py
e

@@ -49,7 +49,7 @@ class VarConBipartiteLayer(MessagePassing):
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
         # Compute scalar variable assignment.
-        var_assignment = self.var_assigment(target)
+        var_assignment = self.var_assigment(source)
 
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
@@ -58,8 +58,8 @@ class VarConBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j, t_i, v_i, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_i, edge_attr], dim=-1))
+    def message(self, x_j, t_i, v_j, edge_attr):
+        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)

### 2021-03-10 paper/main.tex
Cont. implementing new model.
e
MC.

@@
 		\For{$t \text{ in } [T]$}
-		\State For each constraint node $\vec{c}_j$ send $\vec{p}_j$ to adjacent node variable
-		\Statex
 		\State Update each variable node $\vec{v}_i$ based on output $\vec{x}_i$ of oracle using $\vec{p}$
-		\State Send $\vec{v}_i$ to each adjacent constraint, compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
+		\State Send $\vec{v}_i$ to each adjacent constraint
+		\State Compute error signal $\vec{e}_i$ for each constraint $\vec{c}_j$
 		\begin{equation*}
@@
 		\end{equation*}
-		\State Perform gradient descent by $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
+		\State Update $\vec{w}_i \leftarrow (1 - \eta \vec{e}_i) \vec{w}_i$ 
 		\State Normalize weights $\vec{p}_j \leftarrow \nicefrac{\vec{w}_j}{\boldsymbol{\Gamma}(t)} $  for $i$ in $[m]$, where $\boldsymbol{\Gamma}(t) = \sum_{i \in [m]} \vec{w}_i$
@@
 		\For{$t \text{ in } [T]$}
-		%\State \textit{Compute variable embedding:}
-		\State $\vec{V}_j^{(t)} \leftarrow f_{\textsc{Var}}^{(t)} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_j, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$
-		\State $\vec{X}_j^{(t)} \leftarrow f_\textsc{Assn}^{(t)} \hspace{-2pt} \big(\vec{V}_i^{(t-1)} \big)$ for all $j$ in $[n]$ 
+		\State $\vec{V}_j^{(t)} \leftarrow f_{\textsc{Var}}^{(t)} \hspace{-1pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{V}^{(t-1)}_j, \vec{C}^{(t-1)}_j, \vec{p}^{(t-1)}_i, \vec{A}_{ij} \big)\hspace{-1pt} \mid c_i \in N(v_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $j$ in $[n]$
+		\State $\vec{X}_j^{(t)} \leftarrow f_\textsc{Assn}^{(t)} \hspace{-2pt} \big(\vec{V}_j^{(t-1)} \big)$ 
 		\Statex
 		%\State \textit{Compute constraint embedding:}
-		\State $\vec{C}_j^{\hspace{1pt}(t)} \leftarrow f_\textsc{Con}^{(t)} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_j, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_j \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$
+		\State $\vec{C}_i^{\hspace{1pt}(t)} \leftarrow f_\textsc{Con}^{(t)} \hspace{-2pt} \big( \big\{ \hspace{-4.4pt} \big\{ \big( \vec{C}^{(t-1)}_i, \vec{V}^{(t)}_i, \vec{X}^{(t)}_i, \vec{A}_{ij}, \vec{b}_i \big)\hspace{-2pt} \mid v_i \in N(c_j) \big\} \hspace{-4.4pt} \big\} \big)$ for all $i$ in $[m]$
 		%\State $\vec{e}_j^{(t)} \leftarrow \sum_{i \in N(j)} \label{key}\vec{A}_{ji}  \vec{x}_i - \vec{b}_j$
 		%\Statex
-		\State $\vec{p}_{j}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_\textsc{Prob}^{(t)}(\vec{e}^{(t)}))_{j}$
+
+		\State $\vec{p}_{i}^{(t)} \hspace{3pt}\leftarrow \text{softmax}(f_\textsc{Prob}^{(t)}(\vec{e}^{(t)}))_{i}$
 		%\begin{equation*}
@@
 \begin{equation}\label{err}
-\vec{e}_j \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{i \in N(j)} \vec{A}_{ji}  \vec{v}_i \Big) - \vec{b}_j   
+\vec{e}_i \leftarrow \nicefrac{1}{\rho}\,\Big(\sum_{j \in N(i)} \vec{A}_{ij}  \vec{X}_j \Big) - \vec{b}_i   
 \end{equation}
@@
 
-\cm{Somehow show that architecture of Alg. 2 (MWU) is better than using a standard GNN. Idea: Show that MWU can be recovered to show to always get at ferasible solutions.}
+\cm{Somehow show that architecture of Alg.
+2 (MWU) is better than using a standard GNN.
+Idea: Show that MWU can be recovered to show that we always get an (epsilon) feasible solution (on the test data)}
 
@@
 More precisely, we address the following questions:\\
+
+\cm{}
 \begin{description}

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py

@@ -13,123 +13,62 @@ from sklearn.model_selection import train_test_split
 from torch_geometric.data import (InMemoryDataset, Data)
 from torch_geometric.data import DataLoader
 
-import torch_geometric.utils.softmax
-
 import torch
-
 import torch.nn.functional as F
 from torch.nn import BatchNorm1d as BN
-from torch.nn import Sequential, Linear, ReLU, Sigmoid
+from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
 from torch_geometric.nn.inits import reset
+from torch_geometric.utils import degree
+
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
-# Variables to constrains.
-class VarConBipartiteLayer(MessagePassing):
-
-    def __init__(self, edge_dim, dim, var_assigment):
-        super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
-
-        # Combine node and edge features of adjacent nodes.
-        self.nn = Sequential(Linear(3 * dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                             BN(dim))
-
-        # Maps edge features to the same number of components as node features.
-        self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
-
-        # Maps variable embeddings to scalar variable assigment.
-        self.var_assigment = var_assigment
-
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
-        reset(self.edge_encoder)
-
-    def forward(self, source, target, edge_index, edge_attr, rhs, size):
-        # Compute scalar variable assignment.
-        var_assignment = self.var_assigment(source)
-
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
-
-        out = self.propagate(edge_index, x=source, t=target, v=var_assignment, edge_attr=edge_embedding, size=size)
-
-        return out
-
-    def message(self, x_j, t_i, v_j, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
-
-    def __repr__(self):
-        return '{}(nn={})'.format(self.__class__.__name__, self.nn)
-
-
[…]

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -52,7 +52,7 @@ class SimpleBipartiteLayer(MessagePassing):
         row, col = edge_index
 
         #edge_weight = torch.ones((edge_index.size(1), ), device=edge_index.device)
-        deg = degree(row, source.size(0), dtype = source.dtype) + 1
+        deg = degree(row, target.size(0), dtype = target.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -52,7 +52,7 @@ class SimpleBipartiteLayer(MessagePassing):
         row, col = edge_index
 
         #edge_weight = torch.ones((edge_index.size(1), ), device=edge_index.device)
-        deg = degree(row, target.size(0), dtype = target.dtype) + 1
+        deg = degree(col, source.size(0), dtype = source.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -52,7 +52,7 @@ class SimpleBipartiteLayer(MessagePassing):
         row, col = edge_index
 
         #edge_weight = torch.ones((edge_index.size(1), ), device=edge_index.device)
-        deg = degree(col, source.size(0), dtype = source.dtype) + 1
+        deg = degree(row, source.size(0), dtype = source.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -46,6 +46,7 @@ class SimpleBipartiteLayer(MessagePassing):
         reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
+        target = self.linear(target)
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
 
@@ -55,6 +56,8 @@ class SimpleBipartiteLayer(MessagePassing):
         deg = degree(row, source.size(0), dtype = source.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
+
+        exit()
 
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -57,9 +57,10 @@ class SimpleBipartiteLayer(MessagePassing):
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 
-        exit()
+
 
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
+        exit()
 
         out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size, norm=norm)
         out += F.relu(target + self.root_emb.weight) * 1./deg.view(-1,1)

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -53,7 +53,7 @@ class SimpleBipartiteLayer(MessagePassing):
         row, col = edge_index
 
         #edge_weight = torch.ones((edge_index.size(1), ), device=edge_index.device)
-        deg = degree(row, source.size(0), dtype = source.dtype) + 1
+        deg = degree(row, target.size(0), dtype = target.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -60,9 +60,10 @@ class SimpleBipartiteLayer(MessagePassing):
 
 
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
-        exit()
 
         out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size, norm=norm)
+        exit()
+
         out += F.relu(target + self.root_emb.weight) * 1./deg.view(-1,1)
 
         return out

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -52,19 +52,17 @@ class SimpleBipartiteLayer(MessagePassing):
 
         row, col = edge_index
 
-        #edge_weight = torch.ones((edge_index.size(1), ), device=edge_index.device)
         deg = degree(row, target.size(0), dtype = target.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
         deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 
-
-
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
 
         out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size, norm=norm)
-        exit()
+        print("ss")
 
         out += F.relu(target + self.root_emb.weight) * 1./deg.view(-1,1)
+        exit()
 
         return out
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -59,10 +59,8 @@ class SimpleBipartiteLayer(MessagePassing):
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
 
         out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size, norm=norm)
-        print("ss")
 
         out += F.relu(target + self.root_emb.weight) * 1./deg.view(-1,1)
-        exit()
 
         return out
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -54,7 +54,7 @@ class SimpleBipartiteLayer(MessagePassing):
 
         deg = degree(row, target.size(0), dtype = target.dtype) + 1
         deg_inv_sqrt = deg.pow(-0.5)
-        deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
+        #deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
 
         norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
 

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -20,7 +20,7 @@ from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
 from torch_geometric.nn.inits import reset
 from torch_geometric.utils import degree
-
+from torch_sparse import SparseTensor, matmul
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
@@ -37,8 +37,8 @@ class SimpleBipartiteLayer(MessagePassing):
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
-        self.linear = torch.nn.Linear(dim, dim)
-        self.root_emb = torch.nn.Embedding(1, dim)
+        self.lin_l = Linear(dim, dim, bias=True)
+        self.lin_r = Linear(dim, dim, bias=False)
 
         self.reset_parameters()
 
@@ -46,30 +46,27 @@ class SimpleBipartiteLayer(MessagePassing):
         reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
-        target = self.linear(target)
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
 
-        row, col = edge_index
+        out = self.propagate(edge_index, x=source, size=size)
+        out = self.lin_l(out)
 
-        deg = degree(row, target.size(0), dtype = target.dtype) + 1
-        deg_inv_sqrt = deg.pow(-0.5)
-        #deg_inv_sqrt[deg_inv_sqrt == float('inf')] = 0
+        edge_emb = self.edge_encoder(edge_attr)
 
-        norm = deg_inv_sqrt[row] * deg_inv_sqrt[col]
+        out += self.lin_r(target)
 
-        out = self.propagate(edge_index, x=source, t=target, edge_attr=edge_embedding, size=size, norm=norm)
-
-        out += F.relu(target + self.root_emb.weight) * 1./deg.view(-1,1)
+        out = F.normalize(out, p=2., dim=-1)
 
         return out
 
-    def message(self, x_j, t_i, edge_attr, norm):
-        return norm.view(-1, 1) * F.relu(x_j + edge_attr)
+    def message(self, x_j):
+        return x_j
+
+    def message_and_aggregate(self, adj_t, x):
+        adj_t = adj_t.set_value(None, layout=None)
[…]

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -46,11 +46,11 @@ class SimpleBipartiteLayer(MessagePassing):
         reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
-
-        out = self.propagate(edge_index, x=source, size=size)
+        edge_emb = self.edge_encoder(edge_attr)
+        out = self.propagate(edge_index, x=source, size=size, edge_emb = edge_emb)
         out = self.lin_l(out)
 
-        edge_emb = self.edge_encoder(edge_attr)
+
 
         out += self.lin_r(target)
 
@@ -58,8 +58,8 @@ class SimpleBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j):
-        return x_j
+    def message(self, x_j, edge_emb):
+        return x_j + edge_emb
 
     def message_and_aggregate(self, adj_t, x):
         adj_t = adj_t.set_value(None, layout=None)

### 2021-03-10 gnn_models/GCN/mip_bipartite_simple_class.py
MC.

@@ -50,8 +50,6 @@ class SimpleBipartiteLayer(MessagePassing):
         out = self.propagate(edge_index, x=source, size=size, edge_emb = edge_emb)
         out = self.lin_l(out)
 
-
-
         out += self.lin_r(target)
 
         out = F.normalize(out, p=2., dim=-1)
@@ -59,7 +57,7 @@ class SimpleBipartiteLayer(MessagePassing):
         return out
 
     def message(self, x_j, edge_emb):
-        return x_j + edge_emb
+        return F.relu(x_j + edge_emb)
 
     def message_and_aggregate(self, adj_t, x):
         adj_t = adj_t.set_value(None, layout=None)

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -25,10 +25,16 @@ from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
-# Update constraint embeddings based on variable embeddings.
+
+# Variables to constrains.
 class VarConBipartiteLayer(MessagePassing):
+
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+
+        # Combine node and edge features of adjacent nodes.
+        self.nn = Sequential(Linear(3 * dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                             BN(dim))
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
@@ -36,43 +42,29 @@ class VarConBipartiteLayer(MessagePassing):
 
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
-        # Maps variable embeddings + assignment to joint embedding.
-        self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                    BN(dim))
 
-        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                              BN(dim))
-        self.eps = torch.nn.Parameter(torch.Tensor([0]))
-        self.initial_eps = 0
+        self.reset_parameters()
+
+    def reset_parameters(self):
+        reset(self.nn)
+        reset(self.edge_encoder)
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
-        # Map edge features to embeddings with the same number of components as node embeddings.
-        edge_embedding = self.edge_encoder(edge_attr)
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
-        # Compute joint embedding of variable embeddings and scalar variable assignment.
-        new_source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
 
-        # Do the acutal message passing.
-        tmp = self.propagate(edge_index, x=new_source, var_assignment=var_assignment, edge_attr=edge_embedding,
-                             size=size)
[…]

### 2021-03-10 gnn_models/Sage/mip_bipartite_class.py

@@ -25,46 +25,59 @@ from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
-
-# Variables to constrains.
+# Update constraint embeddings based on variable embeddings.
 class VarConBipartiteLayer(MessagePassing):
-
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
-
-        # Combine node and edge features of adjacent nodes.
-        self.nn = Sequential(Linear(3 * dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                             BN(dim))
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
+        self.lin_l = Linear(dim, dim, bias=True)
+        self.lin_r = Linear(dim, dim, bias=False)
+
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
+        # Maps variable embeddings + assignment to joint embedding.
+        self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                    BN(dim))
 
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
-        reset(self.edge_encoder)
+        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                              BN(dim))
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
-        # Compute scalar variable assignment.
-        var_assignment = self.var_assigment(source)
-
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
+        # Compute scalar variable assignment.
+        var_assignment = self.var_assigment(source)
+        # Compute joint embedding of variable embeddings and scalar variable assignment.
+        new_source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
 
[…]

### 2021-03-10 gnn_models/Sage/mip_bipartite_simple_class.py

@@ -30,9 +30,6 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        self.nn = Sequential(Linear(3*dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
-
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
@@ -43,11 +40,12 @@ class SimpleBipartiteLayer(MessagePassing):
         self.reset_parameters()
 
     def reset_parameters(self):
-        reset(self.nn)
+        pass
+        #reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
         edge_emb = self.edge_encoder(edge_attr)
-        out = self.propagate(edge_index, x=source, size=size, edge_emb = edge_emb)
+        out = self.propagate(edge_index, x=source, size=size, edge_emb=edge_emb)
         out = self.lin_l(out)
 
         out += self.lin_r(target)

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -40,6 +40,10 @@ class VarConBipartiteLayer(MessagePassing):
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
+        # Learn joint representation of contraint embedding and error.
+        self.joint_var = Sequential(Linear(dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                    BN(dim))
+
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
 
@@ -52,6 +56,8 @@ class VarConBipartiteLayer(MessagePassing):
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
+
+        new_source = self.joint_con_encoder(torch.cat([source, var_assignment], dim=-1))
 
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)

### 2021-03-10 gnn_models/Sage/mip_bipartite_class.py

@@ -65,7 +65,7 @@ class VarConBipartiteLayer(MessagePassing):
 
         return out
 
-    def message(self, x_j, var_assignment_j, edge_attr):
+    def message(self, x_j, edge_attr):
         return F.relu(x_j + edge_attr)
 
     def update(self, aggr_out):
@@ -127,7 +127,6 @@ class ConVarBipartiteLayer(MessagePassing):
 
         self.lin_l = Linear(dim, dim, bias=True)
         self.lin_r = Linear(dim, dim, bias=False)
-
 
 
     def forward(self, source, target, edge_index, edge_attr, error_con, size):

### 2021-03-10 gnn_models/Sage/mip_bipartite_class.py
MC.

@@ -134,7 +134,7 @@ class ConVarBipartiteLayer(MessagePassing):
         edge_embedding = self.edge_encoder(edge_attr)
         new_source = self.joint_con_encoder(torch.cat([source, error_con], dim=-1))
 
-        out = self.propagate(edge_index, x=new_source, size=size, edge_emb=edge_embedding)
+        out = self.propagate(edge_index, x=new_source, size=size, edge_attr=edge_embedding)
         out = self.lin_l(out)
 
         out += self.lin_r(target)

### 2021-03-10 gnn_models/Sage/mip_bipartite_class.py
MC.

@@ -56,7 +56,7 @@ class VarConBipartiteLayer(MessagePassing):
         # Compute joint embedding of variable embeddings and scalar variable assignment.
         new_source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
 
-        out = self.propagate(edge_index, x=new_source, size=size, edge_emb=edge_embedding)
+        out = self.propagate(edge_index, x=new_source, size=size, edge_attr=edge_embedding)
         out = self.lin_l(out)
 
         out += self.lin_r(target)

### 2021-03-10 gnn_models/Sage/mip_bipartite_class.py
MC.

@@ -144,7 +144,7 @@ class ConVarBipartiteLayer(MessagePassing):
         return out
 
 
-    def message(self, x_j, error_j, edge_attr):
+    def message(self, x_j, edge_attr):
         return F.relu(x_j + edge_attr)
 
     def update(self, aggr_out):

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -57,17 +57,19 @@ class VarConBipartiteLayer(MessagePassing):
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
 
-        new_source = self.joint_con_encoder(torch.cat([source, var_assignment], dim=-1))
+        source = self.joint_var(torch.cat([source, var_assignment], dim=-1))
 
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
 
-        out = self.propagate(edge_index, x=source, t=target, v=var_assignment, edge_attr=edge_embedding, size=size)
+        tmp = self.propagate(edge_index, x=source, edge_attr=edge_embedding, size=size)
+
+        out = self.mlp((1 + self.eps) * target + tmp)
 
         return out
 
-    def message(self, x_j, t_i, v_j, edge_attr):
-        return self.nn(torch.cat([t_i, x_j, v_j, edge_attr], dim=-1))
+    def message(self, x_j, edge_attr):
+        return F.relu(x_j + edge_attr)
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)
@@ -81,11 +83,17 @@ class ErrorLayer(MessagePassing):
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                         BN(dim))
 
+        # Learn joint representation of contraint embedding and error.
+        self.joint_var = Sequential(Linear(dim + dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                                    BN(dim))
+
     def forward(self, source, edge_index, edge_attr, rhs, index, size):
         # Compute scalar variable assignment.
         new_source = self.var_assignment(source)
 
         tmp = self.propagate(edge_index, x=new_source, edge_attr=edge_attr, size=size)
+
+
 
         # Compute residual, i.e., Ax-b.
         out = tmp - rhs
@@ -110,13 +118,16 @@ class ConVarBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(ConVarBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        # Combine node and edge features of adjacent nodes.
-        self.nn = Sequential(Linear(4 * dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                             BN(dim))
 
[…]

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -32,10 +32,6 @@ class VarConBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim, var_assigment):
         super(VarConBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-        # Combine node and edge features of adjacent nodes.
-        self.nn = Sequential(Linear(3 * dim + 1, dim), ReLU(), Linear(dim, dim), ReLU(),
-                             BN(dim))
-
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
@@ -50,7 +46,6 @@ class VarConBipartiteLayer(MessagePassing):
         self.reset_parameters()
 
     def reset_parameters(self):
-        reset(self.nn)
         reset(self.edge_encoder)
 
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
@@ -132,7 +127,7 @@ class ConVarBipartiteLayer(MessagePassing):
         self.reset_parameters()
 
     def reset_parameters(self):
-        reset(self.nn)
+        pass
 
     def forward(self, source, target, edge_index, edge_attr, error_con, size):
         # Map edge features to embeddings with the same number of components as node embeddings.

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -43,6 +43,11 @@ class VarConBipartiteLayer(MessagePassing):
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
 
+
+        self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
+
         self.reset_parameters()
 
     def reset_parameters(self):
@@ -123,6 +128,10 @@ class ConVarBipartiteLayer(MessagePassing):
                                     BN(dim))
 
         self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
+
+
+        self.eps = torch.nn.Parameter(torch.Tensor([0]))
+        self.initial_eps = 0
 
         self.reset_parameters()
 

### 2021-03-10 gnn_models/GIN/mip_bipartite_class.py
MC.

@@ -43,7 +43,6 @@ class VarConBipartiteLayer(MessagePassing):
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
 
-
         self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
         self.eps = torch.nn.Parameter(torch.Tensor([0]))
         self.initial_eps = 0
@@ -93,8 +92,6 @@ class ErrorLayer(MessagePassing):
 
         tmp = self.propagate(edge_index, x=new_source, edge_attr=edge_attr, size=size)
 
-
-
         # Compute residual, i.e., Ax-b.
         out = tmp - rhs
 
@@ -118,7 +115,6 @@ class ConVarBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(ConVarBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
 
-
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
@@ -128,7 +124,6 @@ class ConVarBipartiteLayer(MessagePassing):
                                     BN(dim))
 
         self.mlp = Sequential(Linear(dim, dim), ReLU(), Linear(dim, dim), ReLU(), BN(dim))
-
 
         self.eps = torch.nn.Parameter(torch.Tensor([0]))
         self.initial_eps = 0

### 2021-03-10 gnn_models/GIN/mip_bipartite_simple_class.py

@@ -76,7 +76,7 @@ class SimpleNet(torch.nn.Module):
         self.con_var_4 = SimpleBipartiteLayer(1, hidden)
 
         # MLP used for classification.
-        self.lin1 = Linear(5*hidden, hidden)
+        self.lin1 = Linear(5 * hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
@@ -97,7 +97,6 @@ class SimpleNet(torch.nn.Module):
         self.lin4.reset_parameters()
 
     def forward(self, data):
-
         # Get data of batch.
         var_node_features = data.var_node_features
         con_node_features = data.con_node_features
@@ -112,40 +111,50 @@ class SimpleNet(torch.nn.Module):
         var_node_features_0 = self.var_node_encoder(var_node_features)
         con_node_features_0 = self.con_node_encoder(con_node_features)
 
-
-        con_node_features_1 = F.relu(self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
+        con_node_features_1 = F.relu(
+            self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
                            (num_nodes_var.sum(), num_nodes_con.sum())))
-        var_node_features_1 = F.relu(self.con_var_1(con_node_features_1, var_node_features_0, edge_index_con, edge_features_con,
+        var_node_features_1 = F.relu(
+            self.con_var_1(con_node_features_1, var_node_features_0, edge_index_con, edge_features_con,
                            (num_nodes_con.sum(), num_nodes_var.sum())))
 
-        con_node_features_2 = F.relu(self.var_con_2(var_node_features_1, con_node_features_1, edge_index_var, edge_features_var,
+        con_node_features_2 = F.relu(
+            self.var_con_2(var_node_features_1, con_node_features_1, edge_index_var, edge_features_var,
                            (num_nodes_var.sum(), num_nodes_con.sum())))
-        var_node_features_2 = F.relu(self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
+        var_node_features_2 = F.relu(
+            self.con_var_2(con_node_features_2, var_node_features_1, edge_index_con, edge_features_con,
[…]

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_class.py
MC.

@@ -43,12 +43,6 @@ class VarConBipartiteLayer(MessagePassing):
         # Maps variable embeddings to scalar variable assigment.
         self.var_assigment = var_assigment
 
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
-        reset(self.edge_encoder)
-
     def forward(self, source, target, edge_index, edge_attr, rhs, size):
         # Compute scalar variable assignment.
         var_assignment = self.var_assigment(source)
@@ -111,11 +105,6 @@ class ConVarBipartiteLayer(MessagePassing):
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
-
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, error_con, size):
         # Map edge features to embeddings with the same number of components as node embeddings.

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py

@@ -35,10 +35,6 @@ class SimpleBipartiteLayer(MessagePassing):
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
 
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
         # Map edge features to embeddings with the same number of components as node embeddings.
@@ -109,12 +105,13 @@ class SimpleNet(torch.nn.Module):
 
         x = torch.cat(x_var[:], dim=-1)
 
+        # TODO
         x = F.relu(self.lin1(x))
-        #x = F.dropout(x, p=0.5, training=self.training)
+        x = F.dropout(x, p=0.5, training=self.training)
         x = F.relu(self.lin2(x))
-        #x = F.dropout(x, p=0.5, training=self.training)
+        x = F.dropout(x, p=0.5, training=self.training)
         x = F.relu(self.lin3(x))
-        #x = F.dropout(x, p=0.5, training=self.training)
+        x = F.dropout(x, p=0.5, training=self.training)
         x = self.lin4(x)
         return F.log_softmax(x, dim=-1)
 

### 2021-03-11 gnn_models/Sage/mip_bipartite_class.py

@@ -25,6 +25,7 @@ from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
+
 # Update constraint embeddings based on variable embeddings.
 class VarConBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim, var_assigment):
@@ -71,13 +72,6 @@ class VarConBipartiteLayer(MessagePassing):
     def update(self, aggr_out):
         return aggr_out
 
-    def reset_parameters(self):
-        reset(self.edge_encoder)
-        reset(self.var_assigment)
-        reset(self.node_encoder)
-        reset(self.joint_var)
-        reset(self.mlp)
-        self.eps.data.fill_(self.initial_eps)
 
 
 # Compute error signal.
@@ -88,7 +82,6 @@ class ErrorLayer(MessagePassing):
         self.error_encoder = Sequential(Linear(1, dim), ReLU(), Linear(dim, dim), ReLU(),
                                         BN(dim))
 
-    # TODO: Change back!
     def forward(self, source, edge_index, edge_attr, rhs, index, size):
         # Compute scalar variable assignment.
         new_source = self.var_assignment(source)
@@ -128,7 +121,6 @@ class ConVarBipartiteLayer(MessagePassing):
         self.lin_l = Linear(dim, dim, bias=True)
         self.lin_r = Linear(dim, dim, bias=False)
 
-
     def forward(self, source, target, edge_index, edge_attr, error_con, size):
         # Map edge features to embeddings with the same number of components as node embeddings.
         edge_embedding = self.edge_encoder(edge_attr)
@@ -143,20 +135,11 @@ class ConVarBipartiteLayer(MessagePassing):
 
         return out
 
-
     def message(self, x_j, edge_attr):
         return F.relu(x_j + edge_attr)
 
     def update(self, aggr_out):
         return aggr_out
-
-    def reset_parameters(self):
-        pass
-        # reset(self.node_encoder)
-        # reset(self.edge_encoder)
-        # reset(self.joint_con_encoder)
-        # reset(self.mlp)
-        # self.eps.data.fill_(self.initial_eps)
 
 
 class SimpleNet(torch.nn.Module):
@@ -197,31 +180,6 @@ class SimpleNet(torch.nn.Module):
         self.lin3 = Linear(hidden, hidden)
[…]

### 2021-03-11 gnn_models/Sage/mip_bipartite_simple_class.py

@@ -19,8 +19,7 @@ from torch.nn import BatchNorm1d as BN
 from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
 from torch_geometric.nn.inits import reset
-from torch_geometric.utils import degree
-from torch_sparse import SparseTensor, matmul
+from torch_sparse import matmul
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
@@ -36,12 +35,6 @@ class SimpleBipartiteLayer(MessagePassing):
 
         self.lin_l = Linear(dim, dim, bias=True)
         self.lin_r = Linear(dim, dim, bias=False)
-
-        self.reset_parameters()
-
-    def reset_parameters(self):
-        pass
-        #reset(self.nn)
 
     def forward(self, source, target, edge_index, edge_attr, size):
         edge_emb = self.edge_encoder(edge_attr)
@@ -84,28 +77,12 @@ class SimpleNet(torch.nn.Module):
         self.con_var_4 = SimpleBipartiteLayer(1, hidden)
 
         # MLP used for classification.
-        self.lin1 = Linear(5*hidden, hidden)
+        self.lin1 = Linear(5 * hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
 
-    def reset_parameters(self):
-        self.var_con_1.reset_parameters()
-        self.con_var_1.reset_parameters()
-        self.var_con_2.reset_parameters()
-        self.con_var_2.reset_parameters()
-        self.var_con_3.reset_parameters()
-        self.con_var_3.reset_parameters()
-        self.var_con_4.reset_parameters()
-        self.con_var_4.reset_parameters()
-
-        self.lin1.reset_parameters()
-        self.lin2.reset_parameters()
-        self.lin3.reset_parameters()
-        self.lin4.reset_parameters()
-
     def forward(self, data):
-
         # Get data of batch.
         var_node_features = data.var_node_features
         con_node_features = data.con_node_features
@@ -120,40 +97,50 @@ class SimpleNet(torch.nn.Module):
         var_node_features_0 = self.var_node_encoder(var_node_features)
         con_node_features_0 = self.con_node_encoder(con_node_features)
 
-
[…]

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
MC.

@@ -18,7 +18,6 @@ import torch.nn.functional as F
 from torch.nn import BatchNorm1d as BN
 from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
-from torch_geometric.nn.inits import reset
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
@@ -28,13 +27,12 @@ class SimpleBipartiteLayer(MessagePassing):
     def __init__(self, edge_dim, dim):
         super(SimpleBipartiteLayer, self).__init__(aggr="max", flow="source_to_target")
 
-        self.nn = Sequential(Linear(3*dim, dim), ReLU(), Linear(dim, dim), ReLU(),
-                                       BN(dim))
+        self.nn = Sequential(Linear(3 * dim, dim), ReLU(), Linear(dim, dim), ReLU(),
+                             BN(dim))
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
-
 
     def forward(self, source, target, edge_index, edge_attr, size):
         # Map edge features to embeddings with the same number of components as node embeddings.
@@ -49,7 +47,6 @@ class SimpleBipartiteLayer(MessagePassing):
 
     def __repr__(self):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)
-
 
 
 class SimpleNet(torch.nn.Module):
@@ -72,7 +69,7 @@ class SimpleNet(torch.nn.Module):
         self.layers_var = torch.nn.ModuleList(self.layers_var)
 
         # MLP used for classification.
-        self.lin1 = Linear((num_layers+1)*hidden, hidden)
+        self.lin1 = Linear((num_layers + 1) * hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
@@ -98,25 +95,22 @@ class SimpleNet(torch.nn.Module):
 
         for i in range(self.num_layers):
             x_con.append(F.relu(self.layers_con[i](x_var[-1], x_con[-1], edge_index_var, edge_features_var,
-                               (num_nodes_var.sum(), num_nodes_con.sum()))))
+                                                   (num_nodes_var.sum(), num_nodes_con.sum()))))
 
[…]

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
MC.

@@ -259,12 +259,10 @@ class MyTransform(object):
         return new_data
 
 
-
 path = "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/"
 name = "er_SET2_200_200_alpha_0_75_setParam_100_train_"
 
 results = []
-
 
 # Prepare data.
 path = osp.join(osp.dirname(osp.realpath(__file__)), '.', 'data', 'DS')
@@ -275,7 +273,6 @@ sname = name
 bias_threshold = 0.050
 # Create dataset.
 dataset = GraphDataset(path, data_path, bias_threshold, transform=MyTransform())  # .shuffle()
-
 
 # Split data.
 l = len(dataset)
@@ -330,8 +327,6 @@ def test(loader):
 best_val = 0.0
 test_acc = 0.0
 
-
-
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:
         # Prepare batch loaders.
@@ -343,8 +338,6 @@ for dim in [32, 64, 128]:
         scheduler = torch.optim.lr_scheduler.ReduceLROnPlateau(optimizer, mode='min',
                                                                factor=0.8, patience=10,
                                                                min_lr=0.0000001)
-
-
 
         for epoch in range(1, 100):
 
@@ -363,5 +356,3 @@ for dim in [32, 64, 128]:
             if lr < 0.000001:
                 results.append(test_acc)
                 break
-
-

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
MC.

@@ -326,10 +326,11 @@ def test(loader):
 
 best_val = 0.0
 test_acc = 0.0
+best_hp = []
 
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:
-        # Prepare batch loaders.
+        print(dim, l)
 
         device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
         model = SimpleNet(hidden=dim, num_layers=l).to(device)
@@ -351,8 +352,12 @@ for dim in [32, 64, 128]:
             if val_acc > best_val:
                 best_val = val_acc
                 test_acc = test(test_loader)
+                best_hp = [dim, l, test_acc]
 
             # Break if learning rate is smaller 10**-6.
             if lr < 0.000001:
                 results.append(test_acc)
                 break
+
+
+print(best_hp)

### 2021-03-11 gnn_models/GIN/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -53,32 +53,32 @@ class SimpleBipartiteLayer(MessagePassing):
 
 
 class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden):
+    def __init__(self, hidden, num_layers=5):
         super(SimpleNet, self).__init__()
+        self.num_layers = num_layers
 
         # Embed initial node features.
         self.var_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
         self.con_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
 
         # Bipartite GNN architecture.
-        self.var_con_1 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_1 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_2 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_2 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_3 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_3 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_4 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_4 = SimpleBipartiteLayer(1, hidden)
+        self.layers_con = []
+        self.layers_var = []
+        for i in range(self.num_layers):
+            self.layers_con.append(SimpleBipartiteLayer(1, hidden))
+            self.layers_var.append(SimpleBipartiteLayer(1, hidden))
+
+        self.layers_con = torch.nn.ModuleList(self.layers_con)
+        self.layers_var = torch.nn.ModuleList(self.layers_var)
 
         # MLP used for classification.
-        self.lin1 = Linear(5 * hidden, hidden)
+        self.lin1 = Linear((num_layers + 1) * hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
 
-
-
     def forward(self, data):
+
         # Get data of batch.
         var_node_features = data.var_node_features
         con_node_features = data.con_node_features
@@ -93,44 +93,21 @@ class SimpleNet(torch.nn.Module):
         var_node_features_0 = self.var_node_encoder(var_node_features)
         con_node_features_0 = self.con_node_encoder(con_node_features)
 
-        con_node_features_1 = F.relu(
-            self.var_con_1(var_node_features_0, con_node_features_0, edge_index_var, edge_features_var,
[…]

### 2021-03-11 gnn_models/Sage/mip_bipartite_simple_class.py

@@ -58,31 +58,34 @@ class SimpleBipartiteLayer(MessagePassing):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)
 
 
+
 class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden):
+    def __init__(self, hidden, num_layers=5):
         super(SimpleNet, self).__init__()
+        self.num_layers = num_layers
 
         # Embed initial node features.
         self.var_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
         self.con_node_encoder = Sequential(Linear(2, hidden), ReLU(), Linear(hidden, hidden))
 
         # Bipartite GNN architecture.
-        self.var_con_1 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_1 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_2 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_2 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_3 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_3 = SimpleBipartiteLayer(1, hidden)
-        self.var_con_4 = SimpleBipartiteLayer(1, hidden)
-        self.con_var_4 = SimpleBipartiteLayer(1, hidden)
+        self.layers_con = []
+        self.layers_var = []
+        for i in range(self.num_layers):
+            self.layers_con.append(SimpleBipartiteLayer(1, hidden))
+            self.layers_var.append(SimpleBipartiteLayer(1, hidden))
+
+        self.layers_con = torch.nn.ModuleList(self.layers_con)
+        self.layers_var = torch.nn.ModuleList(self.layers_var)
 
         # MLP used for classification.
-        self.lin1 = Linear(5 * hidden, hidden)
+        self.lin1 = Linear((num_layers + 1) * hidden, hidden)
         self.lin2 = Linear(hidden, hidden)
         self.lin3 = Linear(hidden, hidden)
         self.lin4 = Linear(hidden, 2)
 
     def forward(self, data):
+
         # Get data of batch.
         var_node_features = data.var_node_features
         con_node_features = data.con_node_features
@@ -97,44 +100,21 @@ class SimpleNet(torch.nn.Module):
         var_node_features_0 = self.var_node_encoder(var_node_features)
         con_node_features_0 = self.con_node_encoder(con_node_features)
 
-        con_node_features_1 = F.relu(
[…]

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -23,9 +23,8 @@ device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
 class SimpleBipartiteLayer(MessagePassing):
-
-    def __init__(self, edge_dim, dim):
-        super(SimpleBipartiteLayer, self).__init__(aggr="max", flow="source_to_target")
+    def __init__(self, edge_dim, dim, aggr):
+        super(SimpleBipartiteLayer, self).__init__(aggr=aggr, flow="source_to_target")
 
         self.nn = Sequential(Linear(3 * dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                              BN(dim))
@@ -50,7 +49,7 @@ class SimpleBipartiteLayer(MessagePassing):
 
 
 class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden, num_layers=5):
+    def __init__(self, hidden, aggr, num_layers):
         super(SimpleNet, self).__init__()
         self.num_layers = num_layers
 
@@ -62,8 +61,8 @@ class SimpleNet(torch.nn.Module):
         self.layers_con = []
         self.layers_var = []
         for i in range(self.num_layers):
-            self.layers_con.append(SimpleBipartiteLayer(1, hidden))
-            self.layers_var.append(SimpleBipartiteLayer(1, hidden))
+            self.layers_con.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
+            self.layers_var.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
 
         self.layers_con = torch.nn.ModuleList(self.layers_con)
         self.layers_var = torch.nn.ModuleList(self.layers_var)
@@ -330,34 +329,35 @@ best_hp = []
 
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:
-        print(dim, l)
+        for aggr in ["min", "max", "add", "mean"]:
+            print(dim, l, aggr)
 
-        device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
-        model = SimpleNet(hidden=dim, num_layers=l).to(device)
-        optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
+            device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
+            model = SimpleNet(hidden=dim, num_layers=l, aggr = aggr).to(device)
+            optimizer = torch.optim.Adam(model.parameters(), lr=0.001)
[…]

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -329,7 +329,7 @@ best_hp = []
 
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:
-        for aggr in ["min", "max", "add", "mean"]:
+        for aggr in ["max", "add", "mean"]:
             print(dim, l, aggr)
 
             device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -352,7 +352,7 @@ for dim in [32, 64, 128]:
                 if val_acc > best_val:
                     best_val = val_acc
                     test_acc = test(test_loader)
-                    best_hp = [dim, l, test_acc]
+                    best_hp = [dim, l, aggr, test_acc]
 
                 # Break if learning rate is smaller 10**-6.
                 if lr < 0.000001:

### 2021-03-11 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -314,7 +314,6 @@ def test(loader):
 
     for data in loader:
         data = data.to(device)
-        # pred, err, cost = model(data)
         pred = model(data)
         pred = pred.max(dim=1)[1]
         correct += pred.eq(data.y).float().mean().item()
@@ -358,6 +357,5 @@ for dim in [32, 64, 128]:
                 if lr < 0.000001:
                     results.append(test_acc)
                     break
-
 
 print(best_hp)

### 2021-03-11 gnn_models/GIN/mip_bipartite_simple_class.py

@@ -24,8 +24,8 @@ device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
 class SimpleBipartiteLayer(MessagePassing):
-    def __init__(self, edge_dim, dim):
-        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+    def __init__(self, edge_dim, dim, aggr):
+        super(SimpleBipartiteLayer, self).__init__(aggr=aggr, flow="source_to_target")
 
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
                                        BN(dim))
@@ -53,7 +53,7 @@ class SimpleBipartiteLayer(MessagePassing):
 
 
 class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden, num_layers=5):
+    def __init__(self, hidden, aggr, num_layers):
         super(SimpleNet, self).__init__()
         self.num_layers = num_layers
 
@@ -65,8 +65,8 @@ class SimpleNet(torch.nn.Module):
         self.layers_con = []
         self.layers_var = []
         for i in range(self.num_layers):
-            self.layers_con.append(SimpleBipartiteLayer(1, hidden))
-            self.layers_var.append(SimpleBipartiteLayer(1, hidden))
+            self.layers_con.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
+            self.layers_var.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
 
         self.layers_con = torch.nn.ModuleList(self.layers_con)
         self.layers_var = torch.nn.ModuleList(self.layers_var)
@@ -117,8 +117,7 @@ class SimpleNet(torch.nn.Module):
 
 # Preprocessing to create Torch dataset.
 class GraphDataset(InMemoryDataset):
-    def __init__(self, root, data_path, bias_threshold, transform=None, pre_transform=None,
-                 pre_filter=None):
+    def __init__(self, root, data_path, bias_threshold, transform=None, pre_transform=None, pre_filter=None):
         super(GraphDataset, self).__init__(root, transform, pre_transform, pre_filter)
         self.data, self.slices = torch.load(self.processed_paths[0])
         self.data_path = data_path
@@ -333,35 +332,36 @@ best_hp = []
 
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:
-        print(dim, l)
[…]

### 2021-03-11 gnn_models/Sage/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -18,16 +18,14 @@ import torch.nn.functional as F
 from torch.nn import BatchNorm1d as BN
 from torch.nn import Sequential, Linear, ReLU
 from torch_geometric.nn import MessagePassing
-from torch_geometric.nn.inits import reset
 from torch_sparse import matmul
 
 device = torch.device('cuda' if torch.cuda.is_available() else 'cpu')
 
 
 class SimpleBipartiteLayer(MessagePassing):
-
-    def __init__(self, edge_dim, dim):
-        super(SimpleBipartiteLayer, self).__init__(aggr="add", flow="source_to_target")
+    def __init__(self, edge_dim, dim, aggr):
+        super(SimpleBipartiteLayer, self).__init__(aggr=aggr, flow="source_to_target")
 
         # Maps edge features to the same number of components as node features.
         self.edge_encoder = Sequential(Linear(edge_dim, dim), ReLU(), Linear(dim, dim), ReLU(),
@@ -58,9 +56,8 @@ class SimpleBipartiteLayer(MessagePassing):
         return '{}(nn={})'.format(self.__class__.__name__, self.nn)
 
 
-
 class SimpleNet(torch.nn.Module):
-    def __init__(self, hidden, num_layers=5):
+    def __init__(self, hidden, aggr, num_layers):
         super(SimpleNet, self).__init__()
         self.num_layers = num_layers
 
@@ -72,8 +69,8 @@ class SimpleNet(torch.nn.Module):
         self.layers_con = []
         self.layers_var = []
         for i in range(self.num_layers):
-            self.layers_con.append(SimpleBipartiteLayer(1, hidden))
-            self.layers_var.append(SimpleBipartiteLayer(1, hidden))
+            self.layers_con.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
+            self.layers_var.append(SimpleBipartiteLayer(1, hidden, aggr=aggr))
 
         self.layers_con = torch.nn.ModuleList(self.layers_con)
         self.layers_var = torch.nn.ModuleList(self.layers_var)
@@ -269,8 +266,6 @@ class MyTransform(object):
         return new_data
 
 
-
-
 path = "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/"
 name = "er_SET2_200_200_alpha_0_75_setParam_100_train_"
 
@@ -327,7 +322,6 @@ def test(loader):
 
     for data in loader:
         data = data.to(device)
[…]

### 2021-03-12 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -258,8 +258,39 @@ class MyTransform(object):
         return new_data
 
 
-path = "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/"
-name = "er_SET2_200_200_alpha_0_75_setParam_100_train_"
+print(sys.argv[1])
+exit()
+
+
+file_list = [
+    "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/",
+    "../../DATA1/er_SET2/200_200/alpha_0.25_setParam_100/train/",
+    "../../DATA1/er_SET2/200_200/alpha_0.5_setParam_100/train/",
+    "../../DATA1/er_SET2/300_300/alpha_0.75_setParam_100/train/",
+    "../../DATA1/er_SET2/300_300/alpha_0.25_setParam_100/train/",
+    "../../DATA1/er_SET2/300_300/alpha_0.5_setParam_100/train/",
+    "../../DATA1/er_SET1/400_400/alpha_0.75_setParam_100/train/",
+    "../../DATA1/er_SET1/400_400/alpha_0.5_setParam_100/train/",
+    # "../../DATA1/er_SET1/400_400/alpha_0.25_setParam_100/train/",
+]
+
+name_list = [
+    "er_SET2_200_200_alpha_0_75_setParam_100_train",
+    "er_SET2_200_200_alpha_0_25_setParam_100_train",
+    "er_SET2_200_200_alpha_0_5_setParam_100_train",
+    "er_SET2_300_300_alpha_0_75_setParam_100_train",
+    "er_SET2_300_300_alpha_0_25_setParam_100_train",
+    "er_SET2_300_300_alpha_0_5_setParam_100_train",
+    "er_SET1_400_400_alpha_0_75_setParam_100_train",
+    "er_SET1_400_400_alpha_0_5_setParam_100_train",
+    # "er_SET1_400_400_alpha_0_25_setParam_100_train",
+]
+
+
+
+
+path = file_list[i]
+name = name_list[i]
 
 results = []
 
@@ -325,6 +356,7 @@ def test(loader):
 best_val = 0.0
 test_acc = 0.0
 best_hp = []
+
 
 for dim in [32, 64, 128]:
     for l in [2, 3, 4, 5]:

### 2021-03-12 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -259,8 +259,7 @@ class MyTransform(object):
 
 
 print(sys.argv[1])
-exit()
-
+i = int(sys.argv[1])
 
 file_list = [
     "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/",

### 2021-03-12 gnn_models/EdgeConv/mip_bipartite_simple_class.py
Added hyperparameter opt. using val. set.

@@ -261,6 +261,8 @@ class MyTransform(object):
 print(sys.argv[1])
 i = int(sys.argv[1])
 
+
+
 file_list = [
     "../../DATA1/er_SET2/200_200/alpha_0.75_setParam_100/train/",
     "../../DATA1/er_SET2/200_200/alpha_0.25_setParam_100/train/",
@@ -285,7 +287,7 @@ name_list = [
     # "er_SET1_400_400_alpha_0_25_setParam_100_train",
 ]
 
-
+print(name_list[i])
 
 
 path = file_list[i]
